---
title: "20220906_Bipartite_example"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

1. Reads in a standard bipartite dataset (Southern women?) 

2. Reads in/constructs some people and even covariates (these could be created artificially if they do not come with the dataset) 

3. Formats data in the form that statnet wants it (in particular, print out the dimensions of the affiliation matrix - rectangular? - and any other meta information available; are ties directed or not?) 

4. Specifies a reasonable bipartite ERGM (check the ERGM book but a good model would require an alternating 4-path statistic and possibly some degree-based statistics) 

5. Runs the estimation 

6. Prints output and checks convergence

In addition, it would be good if there was then an additional section:


7. Set an element to missing, e.g. AFF[1,2] <- NA 

8. Rerun the ergm estimation routine 

9. See if it worked and produced an ANOVA table

### Reading in data

Using the 'latentnet' package which has the dataset in it.

The dataset follows 18 women over a 9-month period where they all met each other across 14 informal social events. The data records which women met for which events.

```{r read data}
# reading packages
library(latentnet)
library(here)
library(igraph)

# read in the data
data(davis)

# plot it
adjmat = as.matrix(davis)
plotbip = graph_from_incidence_matrix(adjmat)

# set node type and colour
V(plotbip)$color <- c("orange", "steel blue")[V(plotbip)$type+1]
V(plotbip)$shape <- c("circle", "square")[V(plotbip)$type+1]
V(plotbip)$label <- ""
V(plotbip)$label.cex=.4
V(plotbip)$label.font=2



# and plot it
plot(plotbip, vertex.label.color="white", vertex.size=(2-V(plotbip)$type)*8, layout = layout_as_bipartite) 

# without igraph
plot(davis, 
     displaylabels=TRUE,
     vertex.col = c(rep("Red", 18), rep("Green", 14)),
     vertex.sides = 4*c(rep(10, 18), rep(1, 14)), 
     vertex.cex = c(rep(3, 18), rep(3, 14)),
     label.cex = 0.4, 
     label.pos = 5)

```

### Generating attributes and formatting

```{r making attributes}
# fix seed
set.seed(420)

# randomly generating binary attributes for the people and events
peopleAtt = sample(c(0,1), 18, replace = TRUE)
eventAtt = sample(c(0,1), 14, replace = TRUE)

# set these attributes

# for women
network::set.vertex.attribute(x = davis, 
                              attrname = "randAttPeople",
                              value = peopleAtt,
                              v = 1:18)

# for events
network::set.vertex.attribute(x = davis, 
                              attrname = "randAttEvent",
                              value = eventAtt,
                              v = 19:32)

```

### Brief inspection and ergm time

```{r formatting}
# Obtain women's names from network using %v% operator
names <- (davis %v% "vertex.names")[1:18]

# Create list where each item is an "edge"; look at first 5 of them
apply(adjmat, 2, function(event) names[event==1])[1:5]

# summary with an ergm formula reports the network's observed statistics
# represents the degree for each woman
summary(davis ~ sociality(nodes = 1:18))


## Commented out sociality
# # ergm
# fit1 <- ergm(davis ~ sociality(nodes = 1:18) + b2star(3))
# 
# summary(fit1)
# 
# # with a nodal covariate
# fit2 <- ergm(davis ~ b2star(3) + b2factor("randAttEvent") + sociality(nodes = 1:18))
# 
# summary(fit2)

# with multipe nodal covariates?
fit3 <- ergm(davis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople"))

summary(fit3)

# 4 cycle?
fit4 <- ergm(davis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople") + cycle(4))

summary(fit4)

# alternaaating
fit5 <- ergm(davis ~ gwb1degree(log(2), fixed = TRUE) +
               gwb1dsp(log(2), fixed = TRUE) +
               gwb2dsp(log(2), fixed = TRUE) + 
               b2factor("randAttEvent") + 
               b1factor("randAttPeople"))

summary(fit5)

fit6 <- ergm(davis ~ gwb2degree(log(2), fixed = TRUE) +
               gwb1dsp(log(2), fixed = TRUE) +
               gwb2dsp(log(2), fixed = TRUE) +
               b2factor("randAttEvent") +
               b1factor("randAttPeople"))

summary(fit6)
```


### Now with missingness

```{r miss}
# set an element to missing
missAdj = adjmat
missAdj[1,2] = NA

# set network
missDavis = as.network(missAdj)

# set these attributes
# for women
network::set.vertex.attribute(x = missDavis, 
                              attrname = "randAttPeople",
                              value = peopleAtt,
                              v = 1:18)

# for events
network::set.vertex.attribute(x = missDavis, 
                              attrname = "randAttEvent",
                              value = eventAtt,
                              v = 19:32)

## Commented out sociality
# # rerun ergms
# fitm1 <- ergm(missDavis ~ sociality(nodes = 1:18) + b2star(3))
# 
# summary(fitm1)
# 
# # with a nodal covariate
# fitm2 <- ergm(missDavis ~ b2star(3) + b2factor("randAttEvent") + sociality(nodes = 1:18))
# 
# summary(fitm2)

# with multipe nodal covariates?
fitm3 <- ergm(missDavis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople"))

summary(fitm3)

# 4 cycle?
fitm4 <- ergm(missDavis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople") + cycle(4))

summary(fitm4)

# alternaaating
fitm5 <- ergm(missDavis ~ gwb1degree(log(2), fixed = TRUE) +
                gwb1dsp(log(2), fixed = TRUE) +
                gwb2dsp(log(2), fixed = TRUE) +
                b2factor("randAttEvent") +
                b1factor("randAttPeople"))

summary(fitm5)

fitm6 <- ergm(missDavis ~ gwb2degree(log(2), fixed = TRUE) +
                gwb1dsp(log(2), fixed = TRUE) +
                gwb2dsp(log(2), fixed = TRUE) +
                b2factor("randAttEvent") +
                b1factor("randAttPeople"))

summary(fitm6)


```

### One row is missing

```{r row miss}
# set a row to missing
missRowAdj = adjmat
missRowAdj[1,] = NA

# set network
missRowDavis = as.network(missRowAdj)

# set these attributes
# for women
network::set.vertex.attribute(x = missRowDavis, 
                              attrname = "randAttPeople",
                              value = peopleAtt,
                              v = 1:18)

# for events
network::set.vertex.attribute(x = missRowDavis, 
                              attrname = "randAttEvent",
                              value = eventAtt,
                              v = 19:32)

# sociality won't work here.

# rerun ergms
#fitmr1 <- ergm(missRowDavis ~ sociality(nodes = 1:18) + b2star(3))

#summary(fitmr1)

# with a nodal covariate
#fitmr2 <- ergm(missRowDavis ~ b2star(3) + b2factor("randAttEvent") + sociality(nodes = 1:18))

#summary(fitmr2)

# with multipe nodal covariates?
fitmr3 <- ergm(missRowDavis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople"))

summary(fitmr3)

# 4 cycle?
fitmr4 <- ergm(missRowDavis ~ b2star(3) + b2factor("randAttEvent") + b1factor("randAttPeople") + cycle(4))

summary(fitmr4)

# alternaaating
fitmr5 <- ergm(missRowDavis ~ gwb1degree(log(2), fixed = TRUE) +
                 gwb1dsp(log(2), fixed = TRUE) +
                 gwb2dsp(log(2), fixed = TRUE) +
                 b2factor("randAttEvent") +
                 b1factor("randAttPeople"))

summary(fitmr5)

fitmr6 <- ergm(missRowDavis ~ gwb2degree(log(2), fixed = TRUE) +
                 gwb1dsp(log(2), fixed = TRUE) +
                 gwb2dsp(log(2), fixed = TRUE) +
                 b2factor("randAttEvent") +
                 b1factor("randAttPeople"))

summary(fitmr6)
```
