---
title: "20220107_deletion_sims"
author: "Jon Januar"
date: "07/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document is meant to simulate the deletion approach to handling missing data where missing values are set to 0.

Conceptually, this is a bit of problem as not all missing ties are non-ties.

Observed non-ties are useful as they tell us about the absence of a tie. Missing ties are missing perhaps by design, by some systematic pattern of missingness, by random participant woes, or by measurement error.

This document will generate some graphs with increasing complexity and try to describe what the effects of setting missing ties to 0 are in terms of the resulting statistical model.

## Loading stuff

```{r degradeNet fn, eval = T, warning = F, error = F, message = F}
# load libraries
library(sna)
library(network)
library(ergm)

# degrade net function from previous script
degradeNet <- function(graph, propMiss, directed = TRUE){
  
  ## degradeNet(graph, propMiss) takes a graph and replaces the observed graph ties with missing 
  ## values(NA). This function does not handle actor non-response as it only works off the observed
  ## network ties. Works with undirected networks.
  ##
  ## Input:
  ## - graph:    An adjacency matrix describing a graph. There shouldn't
  ##             be any missing values in this adjacency matrix yet.
  ##             Should still work if there were though. I think.
  ## - propMiss: A numeric value to indicate the proportion of missingness
  ##             that will be imposed on the observed network.
  ##             Is bounded between 0 and 1.
  ## - directed: A logical value to indicate if it's a directed or
  ##             undirected network. Default is set to directed.
  ##
  ## Output: 
  ## - A degraded network with missing ties where observed ties once were.
  ##   Note that it only handles item non-response for now. Given the inputs,
  ##   the missing values would be ~'propMiss'% of the observed tie variables in 'graph'.
  
  ## spit out an error if the directed argument is misspecified
  if(directed != TRUE & !isSymmetric(graph)){
    stop("The undirected network doesn't have a symmetric matrix")
  }
  
  ## spit out an error if the proportion of missingness exceeds bounds
  if(propMiss > 1 | propMiss < 0){
    stop("The proportion of missingness exceeds bounds")
  }
  
  # grab the number of nodes
  n = nrow(graph)
  
  # make a n x n matrix containing randomly generated values between 0 and 1
  missThresh = matrix(data = runif(n^2, min = 0, max = 1),
                      nrow = n,
                      ncol = n)
  
  # index which of the ties are going to be missing
  missTies = missThresh <= propMiss
  
  # copy the graph to punch holes in it
  degradedGraph = graph
  
  if( directed == FALSE ){
    # this atrocious line of code replaces the upper triangle of the undirected graph with missing values
    degradedGraph[upper.tri(graph)][missTies[upper.tri(missTies)]] = NA

    # symmetrise
    degradedGraph[lower.tri(degradedGraph)] = 0           # empty lower triangle
    degradedGraph = degradedGraph + t(degradedGraph)      # add the transpose
  } else {
    # punch holes
    degradedGraph[missTies] = NA
  }
  
  # return the degraded graph
  return(degradedGraph)
}
```

## Random graph generation

```{r berngraphs}
# Just a basic bernoulli graph
bernGraph = rgraph(n = 100,
                   tprob = 0.05)

# degrade and delete
degrBernGraph = degradeNet(graph = bernGraph,
                           propMiss = 0.25,
                           directed = TRUE)

degrBernGraph[is.na(degrBernGraph)] = 0

## let's compute some diagnostics
# degree distribution
bernDegs = degree(dat = bernGraph,
                  gmode = "digraph")
hist(bernDegs,
     xlab = "Degrees",
     ylab = "Frequency",
     main = "Degree distribution: undegraded")

# degree centralisation
centralization(dat = bernGraph,
               FUN = degree,
               mode = "digraph")

# connectivity
# tabulate geodesic distances
gDist = table(geodist(dat = bernGraph)$gdist[upper.tri(geodist(bernGraph)$gdist)])

# plot
plot(gDist,
     xlab = "Geodesic distances",
     ylab = "Frequency",
     main = "Geodesic distances: undegraded")

# do it again for the degraded graph
# degree distribution
bernDegs = degree(dat = degrBernGraph,
                  gmode = "digraph")
hist(bernDegs,
     xlab = "Degrees",
     ylab = "Frequency",
     main = "Degree distribution: degraded 0.25")

# degree centralisation
centralization(dat = degrBernGraph,
               FUN = degree,
               mode = "digraph")

# connectivity
# tabulate geodesic distances
gDist = table(geodist(dat = degrBernGraph)$gdist[upper.tri(geodist(degrBernGraph)$gdist)])

# plot
plot(gDist,
     xlab = "Geodesic distances",
     ylab = "Frequency",
     main = "Geodesic distances: degraded 0.25")

## increase missingness, with fixed graph
# apply degradation to all networks with varying missingness proportions
missProps = seq(from = 0.1, to = 0.7, by = 0.1)

# prepare empty structures
degrBernGraphs = array(data = NA, 
                       dim = c(100,100,7))

# loop?
for(missIndex in 1:length(missProps)){
  # degrade
  degrBernGraphs[,,missIndex] = degradeNet(graph = bernGraph,
                                           propMiss = missProps[missIndex],
                                           directed = TRUE)
}

# missing case deletion for the array
degrBernGraphs[is.na(degrBernGraphs)] = 0

# diagnostics?
# TODO: neaten this. Unloop this.
for(missIndex in 1:length(missProps)){
  
  # choose graph
  chosenGraph = degrBernGraphs[,,missIndex]
  
  # plot graph
  gplot(chosenGraph,
        xlab = paste("Degraded", missProps[missIndex]))
  
  # degree distribution
  bernDegs = degree(dat = chosenGraph,
                    gmode = "digraph")
  hist(bernDegs,
       xlab = "Degrees",
       ylab = "Frequency",
       main = paste("Degree distribution: degraded", missProps[missIndex]))

  # degree centralisation 
  centralization(dat = chosenGraph,
                 FUN = degree,
                 mode = "digraph")

  # connectivity
  # generate geodesic distances
  gDist = geodist(dat = chosenGraph)$gdist[upper.tri(geodist(chosenGraph)$gdist)]
  
  # table only finite ones
  gDistTable = table(gDist[is.finite(gDist)])

  # plot
  plot(gDistTable,
       xlab = "Geodesic distances",
       ylab = "Frequency",
       main = paste("Degree distribution: degraded", missProps[missIndex]))
}

```



















