---
title: "20220520_Sageman_Noordin_ERGMs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading in Sageman data

```{r packages, eval = T, warning = F, error = F, message = F}
# load packages
library('igraph')
library('sna')
library('ergm')
library('network')
library('here')
```


```{r sageman data}
# Read adjacency matrix
SagemanAdjacencyMatrix <- read.csv(here("../Data/SagemanNoordin/sagemanAdjacency.csv"), header=FALSE)

# there are a lot of attributes (you may get a list of what they are from me)
ADJ <- as.matrix(SagemanAdjacencyMatrix)
SageAttributes <- read.csv(here('../Data/SagemanNoordin/sageAttributes.csv'))

# To just get a list of the names of the vertices:
SageNames <- read.csv(here('../Data/SagemanNoordin/vertices.csv'),stringsAsFactors=FALSE)

# a quick way of plotting this network using the 'place where they joined the Jihad':
colnames(ADJ) <- SageNames[,2]
rownames(ADJ) <- SageNames[,2]
SageGraph <- graph.adjacency(ADJ,mode="undirected")

#pdf("SageManPlot.pdf", width=15, height=15)

plot(SageGraph,
     vertex.label.family='sans',
     vertex.label.cex=.5,
     vertex.size=2,
     vertex.frame.color=NA,
     edge.curved=.2,
     vertex.color=SageAttributes$Place.joined.the.jihad)
#dev.off()
```

### Inspecting Sageman data

```{r inspecting Sageman}
# Inspection of attributes
str(SageAttributes)
summary(SageAttributes)

# viewing the network
gplot(dat = ADJ,
      gmode = "graph")

# degree distribution
plot(table(sna::degree(ADJ)), xlab = "Degree", ylab = "Frequency", main = "Degree distribution of the Sageman network")

```

Missing attribute data huh. Points of action:

* MICE (needs to specify a model for the attributes)
* Quick ad hoc solutions (single imputation, complete case analysis?)


### ERGMs!

Remember: the statnet 'ergm' function assumes MAR.

```{r sageman ergms}
# very roughly using single imputation for an attribute
imputedAgeJoined = SageAttributes$Age.joining.the.jihad
imputedAgeJoined[is.na(imputedAgeJoined)] = mean(imputedAgeJoined, na.rm = T)
imputedYearJoined = SageAttributes$Year.joined.the.jihad
imputedYearJoined[is.na(imputedYearJoined)] = mean(imputedYearJoined, na.rm = T)
imputedPlaceJoined = SageAttributes$Place.joined.the.jihad
imputedPlaceJoined[is.na(imputedPlaceJoined)] = mean(imputedPlaceJoined, na.rm = T)

# preparing the network
sagemanNet = as.network(ADJ, directed = FALSE)
sagemanNet %v% 'ageJoined' = imputedAgeJoined
sagemanNet %v% 'yearJoined' = imputedYearJoined
sagemanNet %v% 'placeJoined' = imputedPlaceJoined


# just a random configuration
mod1 = sagemanNet ~ edges + 
   nodecov('ageJoined') +
   nodecov('yearJoined') +
   nodematch('placeJoined')
#   gwdegree(log(2), fixed = TRUE) +
#   gwesp(log(2), fixed = TRUE)

# ergm
summary(ergm(mod1))


### loading the ergm with the specification Johan had
load(here("../Data/SagemanNoordin/sagemanResults.RData"))
load(here("../Data/SagemanNoordin/sagemanImputedData.RData"))

#specification
model.1 <- alqnet ~ edges + isolates +gwesp(decay=log(2), fixed=TRUE)+gwdegree(decay=log(2), fixed=TRUE)+# density
  nodecov( 'place.joined') + # 
  nodematch( 'place.joined')+ # 
  nodematch( 'country.joined')+ # 
  nodecov('educ') + #
  absdiff('educ', pow = 2) +# 
  nodecov('age') + #
  absdiff('age', pow = 2) +#
  nodecov('year.joined') + #
  absdiff('year.joined', pow = 2) +# 
  nodecov('ses') + #
  absdiff('ses', pow = 2) +# 
#  nodemix(  'clump',levels=c(1,2,3))+
#  nodemix( 'school',levels=c(1,2))+
  dyadcov(clump.1.1.dyadcov) + 
  dyadcov(clump.1.2.dyadcov) + 
  dyadcov(clump.1.3.dyadcov) + 
  dyadcov(clump.2.2.dyadcov) + 
  dyadcov(clump.2.3.dyadcov) + 
  dyadcov(clump.3.3.dyadcov) + 
  dyadcov(school.1.1.dyadcov) + 
  dyadcov(school.1.2.dyadcov) + 
  dyadcov(school.2.2.dyadcov) + 
  nodematch( 'plbirth')


# results
summary(ans.1)

```

### Introducing missingness

Using a model for the missing data indicator $\mathbf{D}$ that weighs the probability of being a missing value with degree.

A justification for this might be that the more central the person is for the actual network, the more likely their ties with the central person is to be unreported (e.g., for security purposes).

$$\Pr(\mathbf{D}_{ij} = 1) = logistic(\alpha + \beta(\mathbf{X}_{i+} + \mathbf{X}_{+j}) )$$

```{r missmodel, fig.width = 8, fig.height = 5}
#### missing model with arbitrary parameter values
# grab degrees
degCentr = sna::degree(ADJ)

## finagle the parameters such that the mean is ~0.3

# the eqn to solve is beta = (-log(2.33333) - alpha)/mean(degCentr)
alphaVals = seq(from = -10, to = 10)

betaVals = (-log(2.3333333) - alphaVals)/mean(degCentr)

# make up some values for alpha and beta
alpha = -5        # an intercept value,

beta = 0.32377    # this beta value corresponds to the weight of the variable when assigning the probability of missingness


# list out the probabilities
missTieProb = 1/(1 + exp(-alpha - (beta * degCentr)))

# check mean, if it's off it's due to highly connected nodes.
mean(missTieProb)


# let's first make a matrix of missing data indicators with the probabilities we have
# the rbinom function's just a convenient way of doing this, also each actor technically has an implicit ~Bi(n, miss tie prob) amount of missing ties
missDatIndicator = t(replicate(nrow(ADJ), rbinom(length(missTieProb), size = 1, prob = missTieProb)))

# check how many were indicated to be missing
sum(missDatIndicator)

# make some adjustments because undirected network
missDatIndicator[upper.tri(missDatIndicator)] = t(missDatIndicator)[upper.tri(missDatIndicator)]
diag(missDatIndicator) = 0
isSymmetric(missDatIndicator)

# make a table to compare,
compareTab = data.frame(missTieProb = round(missTieProb, digits = 2), IndicatorProbabilities = colMeans(missDatIndicator))
compareTab$difference = compareTab[,1] - compareTab[,2]

# just checking the mean absolute difference 
mean(abs(compareTab$difference))


# check total amount of missing ties after the adjmat adjustments, should be ~80 (20^2 * 0.2), maybe a bit less because of the adjmat adjustments
sum(missDatIndicator)

# and we deplete
degradedNetMNAR = ADJ
degradedNetMNAR[missDatIndicator==1] = NA

# plot side by side
par(mfrow = c(1,2))
coord = gplot(ADJ, xlab = "Sageman net", gmode = "graph")
gplot(degradedNetMNAR, xlab = "MNAR degraded net", gmode = "graph", coord = coord)

# it's quite hard to see, but if we see the average degree centrality and their barplots,

plot(table(sna::degree(ADJ)), xlab = "Degree", ylab = "Frequency",  main = paste("Mean = ",round(mean(sna::degree(ADJ)), 2), " SD = ", round(sd(sna::degree(ADJ)), 2), sep = ""), xlim = c(0,90), ylim = c(0,100))
plot(table(sna::degree(degradedNetMNAR)), xlab = "Degree", ylab = "Frequency",  main = paste("Mean = ",round(mean(sna::degree(degradedNetMNAR)), 2), " SD = ", round(sd(sna::degree(degradedNetMNAR)), 2), sep = ""), xlim = c(0,90), ylim = c(0,100))
```

### Some metrics

```{r missnet Metrics}
# set n
n = nrow(ADJ)

# density
sum(ADJ)/((n * (n-1))/2)

# post-degradation density
sum(degradedNetMNAR, na.rm = T)/((n * (n-1))/2)

# density for the observable ties (e.g., Dij = 0)
sum(degradedNetMNAR, na.rm = T)/sum(missDatIndicator == 0)

# making the degraded network into a network object with covariates
sagemanNetDegraded = as.network(degradedNetMNAR, directed = FALSE)
sagemanNetDegraded %v% 'place.joined' <- alqnet %v% 'place.joined'
sagemanNetDegraded %v% 'age' <- alqnet %v% 'age'
sagemanNetDegraded %v% 'country.joined' <- alqnet %v% 'country.joined'
sagemanNetDegraded %v% 'year.joined' <- alqnet %v% 'year.joined'
sagemanNetDegraded %v% 'age.join' <- alqnet %v% 'age.joined'
sagemanNetDegraded %v% 'educ' <- alqnet %v% 'educ'
sagemanNetDegraded %v% 'clump' <- alqnet %v% 'clump'
sagemanNetDegraded %v% 'school' <- alqnet %v% 'school'
sagemanNetDegraded %v% 'plbirth' <- alqnet %v% 'plbirth'
sagemanNetDegraded %v% 'ses' <- alqnet %v% 'ses'

# triad censes
sna::triad.census(ADJ)
sna::triad.census(sagemanNetDegraded)

```



### ERGM with missing data

```{r missERGM}
# for ease, set to 0
degradedNet0 = ADJ
degradedNet0[missDatIndicator==1] = 0

# making the degraded network into a network object with covariates
sagemanNetDegraded0 = as.network(degradedNet0, directed = FALSE)
sagemanNetDegraded0 %v% 'place.joined' <- alqnet %v% 'place.joined'
sagemanNetDegraded0 %v% 'age' <- alqnet %v% 'age'
sagemanNetDegraded0 %v% 'country.joined' <- alqnet %v% 'country.joined'
sagemanNetDegraded0 %v% 'year.joined' <- alqnet %v% 'year.joined'
sagemanNetDegraded0 %v% 'age.join' <- alqnet %v% 'age.joined'
sagemanNetDegraded0 %v% 'educ' <- alqnet %v% 'educ'
sagemanNetDegraded0 %v% 'clump' <- alqnet %v% 'clump'
sagemanNetDegraded0 %v% 'school' <- alqnet %v% 'school'
sagemanNetDegraded0 %v% 'plbirth' <- alqnet %v% 'plbirth'
sagemanNetDegraded0 %v% 'ses' <- alqnet %v% 'ses'

# same configuration from before, now with the degraded network
model.2 <- sagemanNetDegraded0 ~ edges + isolates +gwesp(decay=log(2), fixed=TRUE)+gwdegree(decay=log(2), fixed=TRUE)+# density
  nodecov( 'place.joined') + # 
  nodematch( 'place.joined')+ # 
  nodematch( 'country.joined')+ # 
  nodecov('educ') + #
  absdiff('educ', pow = 2) +# 
  nodecov('age') + #
  absdiff('age', pow = 2) +#
  nodecov('year.joined') + #
  absdiff('year.joined', pow = 2) +# 
  nodecov('ses') + #
  absdiff('ses', pow = 2) +# 
#  nodemix(  'clump',levels=c(1,2,3))+
#  nodemix( 'school',levels=c(1,2))+
  dyadcov(clump.1.1.dyadcov) + 
  dyadcov(clump.1.2.dyadcov) + 
  dyadcov(clump.1.3.dyadcov) + 
  dyadcov(clump.2.2.dyadcov) + 
  dyadcov(clump.2.3.dyadcov) + 
  dyadcov(clump.3.3.dyadcov) + 
  dyadcov(school.1.1.dyadcov) + 
  dyadcov(school.1.2.dyadcov) + 
  dyadcov(school.2.2.dyadcov) + 
  nodematch( 'plbirth')



load(here("Scripts", "Spartan", "sagemanToddSummary.RData"))

mod2summary

# same configuration from before, now with the degraded network
model.3 <- sagemanNetDegraded ~ edges + isolates +gwesp(decay=log(2), fixed=TRUE)+gwdegree(decay=log(2), fixed=TRUE)+# density
  nodecov( 'place.joined') + # 
  nodematch( 'place.joined')+ # 
  nodematch( 'country.joined')+ # 
  nodecov('educ') + #
  absdiff('educ', pow = 2) +# 
  nodecov('age') + #
  absdiff('age', pow = 2) +#
  nodecov('year.joined') + #
  absdiff('year.joined', pow = 2) +# 
  nodecov('ses') + #
  absdiff('ses', pow = 2) +# 
#  nodemix(  'clump',levels=c(1,2,3))+
#  nodemix( 'school',levels=c(1,2))+
  dyadcov(clump.1.1.dyadcov) + 
  dyadcov(clump.1.2.dyadcov) + 
  dyadcov(clump.1.3.dyadcov) + 
  dyadcov(clump.2.2.dyadcov) + 
  dyadcov(clump.2.3.dyadcov) + 
  dyadcov(clump.3.3.dyadcov) + 
  dyadcov(school.1.1.dyadcov) + 
  dyadcov(school.1.2.dyadcov) + 
  dyadcov(school.2.2.dyadcov) + 
  nodematch( 'plbirth')


load(here("Scripts", "Spartan", "sagemanPeterSummary.RData"))

mod3summary

# print table to html tables
# combine summary tables
combinedTable = cbind(summary(ans.1)$coefs, mod2summary$coefs, mod3summary$coefs)

write.csv(combinedTable, "sagemanCombinedTable.csv")

knitr::kable(combinedTable)


```


### Generating dyadcovs

```{r clump dyadcov}
# need to generate dyadic covariates for clump because simulate and nodemix does weird things

# this should tell us when i,j belong to any of the chosen clumps.
# and since the sageman net is undirected, clump 1,2 == clump 2,1
clump.dyadcov = matrix(0, nrow = nrow(ADJ), ncol = ncol(ADJ))

# listing the clump matrices
clumpMatrices = list()

# one very chunky loop should get us what we want...
clumpList = list(c(1,1), c(1,2), c(1,3), c(1,4), c(2,2), c(2,3), c(2,4), c(3,3), c(3,4), c(4,4))

for(clump in 1:length(clumpList)){
  chosenClump = clumpList[[clump]]
  targetClump = clump.dyadcov

  for(i in 1:nrow(ADJ)){
     clumpi = (alqnet %v% 'clump')[i]
   
    for(j in 1:ncol(ADJ)){
       clumpj = (alqnet %v% 'clump')[j]
     
       if(sum(c(clumpi, clumpj) == chosenClump) == 2 | 
          sum(c(clumpi, clumpj) == c(chosenClump[2], chosenClump[1])) == 2){
        targetClump[i,j] = 1
         } else {targetClump[i,j] = 0}
     }
  }
  
  # save the target clump
  clumpMatrices[[clump]] = targetClump
}
#save(clumpList, clumpMatrices, file = here("Scripts", "Spartan", "sagemanClumpDyadcovs.RData"))

# do the same for school
school.dyadcov = matrix(0, nrow = nrow(ADJ), ncol = ncol(ADJ))

# listing the school matrices
schoolMatrices = list()

# one very chunky loop should get us what we want...
schoolList = list(c(1,1), c(1,2),c(1,3), c(2,2), c(2,3), c(3,3))

for(school in 1:length(schoolList)){
  chosenschool = schoolList[[school]]
  targetschool = school.dyadcov

  for(i in 1:nrow(ADJ)){
     schooli = (alqnet %v% 'school')[i]
   
    for(j in 1:ncol(ADJ)){
       schoolj = (alqnet %v% 'school')[j]
     
       if(sum(c(schooli, schoolj) == chosenschool) == 2 | 
          sum(c(schooli, schoolj) == c(chosenschool[2], chosenschool[1])) == 2){
        targetschool[i,j] = 1
         } else {targetschool[i,j] = 0}
     }
  }
  
  # save the target school
  schoolMatrices[[school]] = targetschool
}
#save(schoolList, schoolMatrices, file = here("Scripts", "Spartan", "sagemanSchoolDyadcovs.RData"))

# label the dyad covs
clump.1.1.dyadcov = clumpMatrices[[1]]
clump.1.2.dyadcov = clumpMatrices[[2]]
clump.1.3.dyadcov = clumpMatrices[[3]]
clump.2.2.dyadcov = clumpMatrices[[5]]
clump.2.3.dyadcov = clumpMatrices[[6]]
clump.3.3.dyadcov = clumpMatrices[[8]]

school.1.1.dyadcov = schoolMatrices[[1]]
school.1.2.dyadcov = schoolMatrices[[2]]
school.2.2.dyadcov = schoolMatrices[[4]]


```


For every edge, verify if the sender/receiver are part of the clumps I specify.

## Loading in the Noordin Top data

For the Noordin Top data, we have multiple definitions of a tie:

* Friendship  
* People by event (bipartite)   
* Event by event (one mode)  
* Classmate  
* Communication  

```{r load noordin}
# loading in friendship ties
FriendNet <- read.csv(here("../Data/SagemanNoordin/friendship.csv"),
                      sep=',',
                      header=TRUE,
                      row.names=1,
                      stringsAsFactors=FALSE)

# Turn into a matrix obj
FriendNetMat <- as.matrix(FriendNet)
rownames(FriendNetMat) <- rownames(FriendNet)
colnames(FriendNetMat) <- colnames(FriendNet)
bnet <- grey(c(0:100)/100)
net <- graph.adjacency(FriendNetMat,mode="undirected")
V(net)$size=igraph::degree(net)/max(igraph::degree(net))*7
gplot(FriendNetMat, gmode = 'graph', xlab = "Friendship")


# View the network
plot(net,
     vertex.color="#8A8A8A",
     edge.curved=.05,
     edge.width=.5,
     edge.color=bnet[30],
     vertex.frame.color=NA,
     vertex.label.family='sans',
     vertex.label.cex=.5, 
     vertex.label.color= 'black')


# people by event
peopleevent <- read.csv(here("../Data/SagemanNoordin/peoplebyevent.csv"), sep=',',row.names=1, header=TRUE, stringsAsFactors=FALSE, check.names=FALSE)
peopleeventMat <- as.matrix(peopleevent)
rownames(peopleeventMat) <- rownames(peopleevent)
colnames(peopleeventMat) <- colnames(peopleevent)
plot(table(rowSums(peopleeventMat)))
gplot(peopleeventMat, 
      gmode = 'twomode',
      xlab = "People by Event",
      usearrows = FALSE)

# Participation network
participGraph <- graph.incidence(peopleeventMat, directed=F, weighted=NULL, multiple=F)
vecColor <- colors()
V(participGraph)$color <- c(rep(vecColor[414],length=nrow(peopleeventMat)), rep(vecColor[76],length=ncol(peopleeventMat)))
V(participGraph)$shape <- c(rep("circle",length=nrow(peopleeventMat)), rep("none",length=ncol(peopleeventMat)))

plot(participGraph, 
     vertex.size=1,
     edge.width=.5,
     edge.curved=.2,
     main="Terrorists by events",
     vertex.label.family='sans',
     vertex.label.cex=.75,
     vertex.label.color= 'black')



### One mode event-by-event network: 
## Q- What is a tie here?
eventonemode <- read.csv(here("../Data/SagemanNoordin/eventbyevent.csv"),
                         sep=',',
                         row.names=1, 
                         header=TRUE, 
                         stringsAsFactors=FALSE, 
                         check.names=FALSE)

bigEventMat <- matrix(0,ncol(peopleeventMat),ncol(peopleeventMat))
rownames(bigEventMat) <- colnames(peopleeventMat)
colnames(bigEventMat) <- colnames(peopleeventMat)
k <-1
for (i in c(1:nrow(eventonemode)))
{
	sender <- which(rownames(bigEventMat)==rownames(eventonemode)[i])
	for (j in c(1:ncol(eventonemode)))
	{
		if (eventonemode[i,j]==1)
		{receiver <- which(rownames(bigEventMat)==colnames(eventonemode)[j])
		bigEventMat[sender,receiver] <- 1
		bigEventMat[receiver, sender] <- 1
		print(paste('tie number ',k,' between ',rownames(eventonemode)[i],' and ',colnames(eventonemode)[j]))
		k <- k+1
}	}
}

net <- graph.adjacency(bigEventMat,mode="undirected")
V(net)$size=igraph::degree(net)/max(igraph::degree(net))*7
plot(net,vertex.color="#8A8A8A",
     edge.curved=.05,
     edge.width=.5,
     edge.color=bnet[30],
     vertex.frame.color=NA ,
     vertex.label.family='sans',
     vertex.label.cex=.75, 
     vertex.label.color= 'black')

########
BigMat <- cbind(FriendNetMat,peopleeventMat)
bottomRow <- cbind(t(peopleeventMat),bigEventMat)
BigMat <-rbind(BigMat,bottomRow)
net <- graph.adjacency(BigMat,mode="undirected")
V(net)$color <- c(rep(vecColor[414],length=nrow(peopleeventMat)), rep(vecColor[76],length=ncol(peopleeventMat)))
V(net)$shape <- c(rep("circle",length=nrow(peopleeventMat)), rep("square",length=ncol(peopleeventMat)))
V(net)$size=igraph::degree(net)/max(igraph::degree(net))*7
plot(net,
     edge.width=.5,
     edge.curved=.2,
     main="The multilevel network of Noordin Top",
     vertex.label.family='sans',
     vertex.label.cex=.75, 
     vertex.label.color= 'black',
     vertex.frame.color=NA)



#### Both of the files below are another type of tie for the Noordin Top network
## Classmate tie
classmates <- read.csv(here("../Data/SagemanNoordin/classmates.csv"), 
                       sep=',',
                       row.names=1,
                       header=TRUE,
                       stringsAsFactors=FALSE,
                       check.names=FALSE)

# Turn into a matrix
classmateMat = as.matrix(classmates)
rownames(classmateMat) <- rownames(classmates)
colnames(classmateMat) <- colnames(classmates)
bnet <- grey(c(0:100)/100)
net <- graph.adjacency(classmateMat,mode="undirected")
V(net)$size=igraph::degree(net)/max(igraph::degree(net))*7
gplot(classmateMat, gmode = 'graph', xlab = "Classmates")


## communication tie
communicate <- read.csv(here("../Data/SagemanNoordin/communication.csv"),
                        sep=',',
                        row.names=1, 
                        header=TRUE, 
                        stringsAsFactors=FALSE, 
                        check.names=FALSE)

# Turn into a matrix
communicateMat = as.matrix(communicate)
rownames(communicateMat) <- rownames(communicate)
colnames(communicateMat) <- colnames(communicate)
bnet <- grey(c(0:100)/100)
net <- graph.adjacency(communicateMat,mode="undirected")
V(net)$size=igraph::degree(net)/max(igraph::degree(net))*7
gplot(communicateMat, gmode = 'graph', xlab = "Communication")



```

### Noordin ERGMs!

```{r noordin ERGMs, eval = F, echo = F}
# preparing the networks
noordFriendNet = as.network(FriendNetMat, directed = FALSE)
noordCommNet = as.network(communicateMat, directed = FALSE)

# some simple ergms
mod1Noord = noordFriendNet ~ edges + 
# isolates +
  gwdegree(decay = log(2), fixed = TRUE) + 
  gwesp(decay = log(2), fixed = TRUE)
  

m1n = ergm(mod1Noord, control = control.ergm(init.method = 'CD', MCMC.burnin = 4000, MCMC.interval = 4000, SAN.maxit = 10))

mod2Noord = noordCommNet ~ edges + 
# isolates +
  gwdegree(decay = log(2), fixed = TRUE) + 
  gwesp(decay = log(2), fixed = TRUE)
  

m2n = ergm(mod2Noord, control = control.ergm(init.method = 'CD', MCMC.burnin = 4000, MCMC.interval = 4000, SAN.maxit = 10))

```


### Missing data

```{r missmodelnoord, fig.width = 8, fig.height = 8, eval = F, echo = F}
# missing model with arbitrary parameter values

# make up some values for alpha and beta
alpha = -1.88  # an intercept value,

beta = 1 # this beta value corresponds to the weight of the variable when assigning the probability of missingness

# grab degrees
degCentr = sna::degree(noordFriendNet)

# scale degree for more stable estimation
scaledDegCentr = degCentr/mean(degCentr)

# finagle the parameters such that the mean is ~0.3

mean(1/(1 + exp(-alpha - (beta * scaledDegCentr))))

# list out the probabilities
missTieProb = 1/(1 + exp(-alpha - (beta * scaledDegCentr)))

# let's first make a matrix of missing data indicators with the probabilities we have
# the rbinom function's just a convenient way of doing this, also each actor technically has an implicit ~Bi(n, miss tie prob) amount of missing ties
missDatIndicator = t(replicate(nrow(noordFriendNet), rbinom(length(missTieProb), size = 1, prob = missTieProb)))

# check how many were indicated to be missing
sum(missDatIndicator)

# make some adjustments because undirected network
missDatIndicator[upper.tri(missDatIndicator)] = t(missDatIndicator)[upper.tri(missDatIndicator)]
diag(missDatIndicator) = 0
isSymmetric(missDatIndicator)

# make a table to compare,
compareTab = data.frame(missTieProb = round(missTieProb, digits = 2), IndicatorProbabilities = colMeans(missDatIndicator))
compareTab$difference = compareTab[,1] - compareTab[,2]

# just checking the mean absolute difference 
mean(abs(compareTab$difference))


# check total amount of missing ties after the adjmat adjustments, should be ~80 (20^2 * 0.2), maybe a bit less because of the adjmat adjustments
sum(missDatIndicator)

# and we deplete
degradedNetMNAR = noordFriendNet
degradedNetMNAR[missDatIndicator==1] = NA

# plot side by side
par(mfrow = c(1,2))
coord = gplot(noordFriendNet, xlab = "Noordin Top net", gmode = "graph")
gplot(degradedNetMNAR, xlab = "MNAR degraded net", gmode = "graph", coord = coord)

# it's quite hard to see, but if we see the average degree centrality and their histograms,
hist(sna::degree(noordFriendNet), main = paste("Mean = ",round(mean(sna::degree(noordFriendNet)), 2), " SD = ", round(sd(sna::degree(noordFriendNet)), 2), sep = ""))
hist(sna::degree(degradedNetMNAR), main = paste("Mean = ",round(mean(sna::degree(degradedNetMNAR)), 2), " SD = ", round(sd(sna::degree(degradedNetMNAR)), 2), sep = ""))
```

### Noordin ERGMs with missing data




## GOFs?



```{r gofs}
# loading model objects
load(here("Scripts", "Spartan", "20220531_sagemanPeterSummary.RData"))
load(here("Scripts", "Spartan", "20220531_sagemanToddSummary.RData"))
load(here("Scripts", "Spartan", "20220531_sagemanFullSummary.RData"))


## simulate networks from a given model.
# needs the ergm object or the formula.



# ## peter simulations, minus nodemix
# peterModel =  sagemanNetDegraded ~ edges + isolates +
#   gwesp(decay=log(2), fixed=TRUE)+
#   gwdegree(decay=log(2), fixed=TRUE)+# density
#   nodecov( 'place.joined') + #
#   nodematch( 'place.joined')+ #
#   nodematch( 'country.joined')+ #
#   nodecov('educ') + #
#   absdiff('educ', pow = 2) +#
#   nodecov('age') + #
#   absdiff('age', pow = 2) +#
#   nodecov('year.joined') + #
#   absdiff('year.joined', pow = 2) +#
#   nodecov('ses') + #
#   absdiff('ses', pow = 2) +#
#   nodematch( 'plbirth')

peterSim = simulate(object = mod3ergm, nsim = 50,
                    control=control.simulate.ergm(MCMC.burnin=1024,MCMC.interval=1024),
                    output='stats')


# ## todd simulations, minus nodemix
# toddModel = sagemanNetDegraded0 ~ edges + isolates +
#   gwesp(decay=log(2), fixed=TRUE)+
#   gwdegree(decay=log(2), fixed=TRUE)+# density
#   nodecov( 'place.joined') + #
#   nodematch( 'place.joined')+ #
#   nodematch( 'country.joined')+ #
#   nodecov('educ') + #
#   absdiff('educ', pow = 2) +#
#   nodecov('age') + #
#   absdiff('age', pow = 2) +#
#   nodecov('year.joined') + #
#   absdiff('year.joined', pow = 2) +#
#   nodecov('ses') + #
#   absdiff('ses', pow = 2) +#
#   nodematch( 'plbirth')

toddSim = simulate(object = mod2ergm, nsim = 50,
                    control=control.simulate.ergm(MCMC.burnin=1024,MCMC.interval=1024),
                    output='stats')

# compare degrees somehow?
gwdegPeter = peterSim[,"gwdeg.fixed.0.693147180559945"]
gwdegTodd = toddSim[,"gwdeg.fixed.0.693147180559945"]

# edges?
edgeCountTodd = toddSim[,"edges"]
edgeCountPeter = peterSim[,"edges"]

# ggplot
library(ggplot2)

# data to plot
gwdegPlotDat = data.frame(gwdeg = c(gwdegPeter, gwdegTodd), model = c(rep("Peter", 50), rep("Todd", 50)))

ggplot(data = gwdegPlotDat, aes(x = gwdeg, fill = model)) +
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity', binwidth = 1) +
    labs(fill="")

# can use a cdf instead to visualise
cdfTodd = ecdf(gwdegTodd)
cdfPeter = ecdf(gwdegPeter)

curve(cdfPeter, xlim = c(450, 650), ylab = "CDF", xlab = "gwDeg count")
curve(cdfTodd, add = TRUE, col = "brown")
legend(x = 450, y = 1, legend = c("Todd", "Peter"), col = c("brown", "black"), lty = c(1,1))

cdfToddEdges = ecdf(edgeCountTodd)
cdfPeterEdges = ecdf(edgeCountPeter)

curve(cdfPeterEdges, xlim = c(280, 900), ylab = "CDF", xlab = "Edge count")
curve(cdfToddEdges, add = TRUE, col = "brown")
legend(x = 280, y = 1, legend = c("Todd", "Peter"), col = c("brown", "black"), lty = c(1,1))

```

