---
title: "20230509_indepMissModels"
author: "Jon Januar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document will contain simulations of some models of a missingness indicator $\mathbf{D|X}$ assuming independence between tie variables. 

We will also be using only undirected ties throughout.

## The 'data'

```{r simuNet}
# generating a simulated network as X
# set number of nodes, choosing 30 arbitrarily
n = 30

# using a uniform dist
simMat = matrix(data = NA, nrow = n, ncol = n)

# fix the diagonal
diag(simMat) = 0

# randomly generate values for all nonzero values (i.e., all off-diagonal elements)
simMat[is.na(simMat)] = runif(sum(is.na(simMat)))

# use some threshold (this would be the density)
threshold = 0.3

# all values above the threshold are not ties
simMat[simMat > threshold] = 0

# all nonzero elements are then ties
simMat[simMat != 0] = 1

# how to approach this symmetrically..?
```



The candidate models for $\mathbf{D}$ in the document are:

1. Erdos-Renyi model

$$\Pr(d_{ij} = 1) = p_{ij},$$

```{r bern model}
# Bernoulli
# I can generate tie probabilities for only one triangle and symmetrise, but I get the feeling I want to acknowledge the other end of the tie variable...

# in any case, this is kind of brute forcing it
erMiss = matrix(data = 0, nrow = n, ncol = n)

# take only one triangle
erMiss[upper.tri(erMiss)] = runif((n*(n-1))/2)

# and symmetrise
erMiss[lower.tri(erMiss)] = t(erMiss)[lower.tri(erMiss)]

# same threshold jig
# use some threshold (this would be the density)
threshold = 0.3

# all values above the threshold are not ties
erMiss[erMiss > threshold] = 0

# all nonzero elements are then ties
erMiss[erMiss != 0] = 1


```

The part to consider here is that I am brute forcing the generation of edges to only be on one triangle instead of accounting for both ends of the edge.

2. Logit regression

$$logit(\Pr(d_{ij} = 1)) = \theta_0 + \theta_1c_i + \theta_2c_j.$$

In this expression, $d_{ij}$ is a missing tie variable in the missingness matrix $\mathbf{D}$. Strictly speaking this would be $\Pr(\mathbf{D} = d_{ij} | \mathbf{X,C})$ with $\mathbf{X}$ representing the observed tie variables (i.e., an adjacency matrix) and $\mathbf{C}$ representing some matrix of covariates for the nodes.

The idea of what's happening here is that the probability of a missing tie variable depends on the effects of both ends of the edge.


```{r logit example}
## Basically what this boils down to is the dependent variable being a vector.
# fix the order of the graph
n = 30

# simultaing some random binary covariates for the 30 nodes
nodeAtt = sample(x = c(0,1), size = n, replace = TRUE, prob = c(0.6, 0.4))

# check
sum(nodeAtt)

# the thing here is that the 'observation' here needs to be the tie variables.
# an n = 30 means n(n-1) tie variables.. so that's 30 *29 = 870

# first, a sequence needs to be made for every possible dyad:
allEdges = data.frame(i = rep(1:n, each = n), j = rep(1:n, times = n))

# remove all loops because we're dealing with simple graphs
allEdges = allEdges[allEdges$i != allEdges$j,]

# this would basically be a fully connected graph
# then we can assign the simulated binary attribute to both ends of the edges
nodesWithAtt = c(1:n)[nodeAtt == 1]

# then we can give each edge the attribute
# make an empty data frame
edgeAtts = data.frame(i = rep(0, times = nrow(allEdges)), j = rep(0, times = nrow(allEdges)))

# and then we indicate which nodes on either end have the simulated binary attribute
edgeAtts$i[allEdges$i %in% nodesWithAtt] = 1
edgeAtts$j[allEdges$j %in% nodesWithAtt] = 1

# we now can simulate a logit regression model for the 
# specify some arbitrary values
theta0 = -2
theta1 = 1
theta2 = 2

# specify the linear combination
d = theta0 + theta1*edgeAtts$i + theta2*edgeAtts$j

# specify the logit link
pr_d = 1/(1 + exp(-d))

# then we can simulate the tie variables with the probabilities we simulated
y = rbinom(n = length(pr_d), size = 1, prob = pr_d)

# can check our result
glm(y ~ i + j, family = "binomial", data = edgeAtts)

# we can then squish this y into a matrix for D
logitMiss = matrix(data = 2, nrow = n, ncol = n)

# specify some value for the diagonal, this value is arbitrary
diag(logitMiss) = 1

# fill all values outside the diagonal with the simulated values
logitMiss[logitMiss != 1] = y

# and remove the diagonal
diag(logitMiss) = 0

# can force the symmetry if necessary
logitMiss[lower.tri(logitMiss)] = t(logitMiss)[lower.tri(logitMiss)]
```


Same problem here: how do I simulate something undirected...? Do I squish the existence of a dyad to a single variable (i.e., dyad-independent?)

3. Beta model

Do I randomly sample from all possible edges?

I need to first generate a degree sequence..

Also, they say the model works primarily with dense graphs (number of edges greater than the number of nodes squared), and is unsure about sparser graphs.

Following Rinaldo et al. (2013)

```{r}
# beta model attempts

# a small network
testMat = matrix(data = sample(c(0,1), size = 25, replace = TRUE), 5, 5)
diag(testMat) = 0

# undirect it
testMat[upper.tri(testMat)] = t(testMat)[upper.tri(testMat)]
rowSums(testMat)

# some beta values (are these supposed to be calculated?)
beta = c(0.5, -0.2, 0.1, 0.1, 0.8)

# empty vector of estimated probability parameters
pEst = c()

# a loop to logit it
for(ind in 1:5){
    pEst[ind] = (exp(beta[ind] + beta[-ind]))/ (1 + exp(beta[ind] + beta[-ind]))
}

# then plugged in a binom to generate degrees
dEst = rbinom(n = nrow(testMat), size = nrow(testMat), prob = pEst)
```


4. Blockmodels


5. Social space models