---
title: "20231114_alaamSims"
author: "Jon Januar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulating an ALAAM

This example's going to be using the London gangs dataset

```{r load data}
# packages
library(here)
library(sna)
library(stringr)

# load in the BayesALAAM
source(here("Scripts", "bayesNetworkRoutines", "MultivarALAAMalt.R"))

# this proof of concept works for simulating an ALAAM,
# now let's try doing this with a UCINet empirical covert network
# load in the london gangs dataset (Net 6)
load(here("Data", "20231006_missNetsEnMasse.RData"))

# take the specific adjmat
exampleMat = adjMatList[[6]]

```

```{r line graph stuff}

### TODO:: check to make sure the function's actually doing what it's supposed to. Ideally figure out a unit test for it
# a function made in May 2022 to translate an adjmat into a line graph, go 2022 me
lineGraph <- function(adjMat, directed = FALSE){
  
  ## lineGraph(adjMat, directed) takes an adjacency matrix and generates its 
  ## corresponding line graph for its edges. 
  ##
  ## Input:
  ## - adjMat:   An adjacency matrix describing a graph. Not sure if missing data 
  ##             will mess with the conversion. 
  ##
  ## - directed: A logical value to indicate whether the graph is directed or not.
  ##
  ## Output:
  ## - The line graph for the input adjacency matrix, stored as another matrix.
  
  ### count the number of edges
  edgeCount = sum(adjMat)
  
  # if undirected, divide in half.
  if (directed == FALSE){
    edgeCount = edgeCount/2
    adjMat[lower.tri(adjMat)] = 0
  }
  
  # make a matrix of indices for edges (basically an edgelist)
  inds = which(adjMat == 1, arr.ind = TRUE)
  
  # order it for readability
  inds = inds[order(inds),]
  
  # make an empty matrix for the edges (represented as nodes)
  lineMat = matrix(data = 0, 
                   nrow = edgeCount,
                   ncol = edgeCount)
  
  # use the edge list to make the line graph matrix
  for(edgeInd in 1:edgeCount){                              # for every edge in the edge list
    tempMat = matrix(data = c(inds %in% inds[edgeInd,]),    # match the edge with the same nodes
                     ncol = 2)    
    tempMat[edgeInd,] = FALSE                               # remove the selected edge in the matches
    lineMat[edgeInd,] = tempMat[,1] + tempMat[,2]           # and put all the edges with the same nodes in the matrix
  }
  
  
  # make a vector of labels for the nodes
  nodeLabel = apply(inds,
                    MARGIN = 1,
                    FUN = toString)
  
  # remove whitespace
  nodeLabel = gsub(" ", "", nodeLabel, fixed = TRUE)
  
  # name the matrix
  rownames(lineMat) = nodeLabel
  
  # return the line graph matrix
  return(lineMat)
}

# grab the line graph
lineTest = lineGraph(adjMat = exampleMat, directed = FALSE)

# what does the line graph look like?
gplot(lineTest, gmode = "graph", main = "Line graph")

# but for the siulation, you don't need an outcome vectorspecified beforehand.. so
emptyLineOutcome = rep(0, times = ncol(lineTest))

# get unique ids for dyadic cov
lineTestEdgeListStr = str_split(rownames(lineTest), pattern = ",")

# reformat into a more friendly data frame
lineTestEdgeList = data.frame(sender = as.numeric(unlist(lapply(lineTestEdgeListStr, FUN = function(x){x[1]}))), 
                              receiver = as.numeric(unlist(lapply(lineTestEdgeListStr, FUN = function(x){x[2]}))))

# some covariates, these need to be specifc to the edge... so they need to be formatted as dyadic covariates
centeredAge = (londonGangsAtt$Age - mean(londonGangsAtt$Age))/sd(londonGangsAtt$Age)

# turn into a 'edge' covariate using the indices in the edge list data frame
centAgeDiffEdgeCov = c()
prisonEdgeCov = c()

# just loop it
for(edgeNo in 1:nrow(lineTestEdgeList)){

  sender = lineTestEdgeList[edgeNo, "sender"]
  receiver = lineTestEdgeList[edgeNo, "receiver"]

  centAgeDiffEdgeCov[edgeNo] = centeredAge[sender] - centeredAge[receiver]
  prisonEdgeCov[edgeNo] = londonGangsAtt$Prison[sender] + londonGangsAtt$Prison[receiver]

}

# since Prison is a binary variable, the dyad cov can be 0, 1 or 2.
# let's keep it to mutual ties for now
prisonEdgeCov[prisonEdgeCov == 2] = 1


# taking prison out for now since it's not that much heterogeneity


# covs
lineAlaamCovs = cbind(centAgeDiffEdgeCov)

# ALAAM stuff
linePrep = prepALAAMdata(y = emptyLineOutcome,
                         ADJ = lineTest,
                         covariates = lineAlaamCovs,
                         directed = FALSE,
                         useDegree = FALSE,
                         contagion = "simple")

# simulate
simAlaamOutcome = simulateALAAM(y = emptyLineOutcome, 
                                EdgeList = linePrep$EdgeList, 
                                RowIn = linePrep$RowIn, 
                                degree = linePrep$degree, 
                                covariates = linePrep$covariates, 
                                NumIterations = 3000,
                                thinning= 10,
                                theta = c(-2, 0.1, 0.1),
                                statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                                returnNet = TRUE,
                                canchange = c(1:nrow(lineTest)),
                                DoSave = FALSE)  
print(simAlaamOutcome)

# check how many edges are sampled
table(simAlaamOutcome$y)



```

```{r multiple cont values}
# #### Set some values for all the models
trials = 1000
 
# ### objects that will contain simulated statistics
# zeroSimStats = matrix(data = 0, nrow = trials, ncol = ncol(lineAlaamCovs) + 2)  # covariates + edges + contagion
# smallSimStats = matrix(data = 0, nrow = trials, ncol = ncol(lineAlaamCovs) + 2)
# largeSimStats = matrix(data = 0, nrow = trials, ncol = ncol(lineAlaamCovs) + 2)
# zeroSampledEdges = matrix(data = 0, nrow = trials, ncol = nrow(lineTest))
# smallSampledEdges = matrix(data = 0, nrow = trials, ncol = nrow(lineTest))
# largeSampledEdges = matrix(data = 0, nrow = trials, ncol = nrow(lineTest))


# set thetas
zeroTheta = c(-0.8, 0, 0.2)


# now do the same for multiple values for contagion
zeroContSim = simulateALAAM(y = emptyLineOutcome, 
                            EdgeList = linePrep$EdgeList, 
                            RowIn = linePrep$RowIn, 
                            degree = linePrep$degree, 
                            covariates = linePrep$covariates, 
                            NumIterations = trials,
                            thinning= 5,
                            theta = zeroTheta,
                            statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                            returnNet = TRUE,
                            canchange = c(1:nrow(lineTest)))
print(zeroContSim)

# check how many edges are sampled
table(zeroContSim$y)


## do this multiple times to get an approximate range of simulated statistics
  # using the same objects so...
zeroStatSim = suppressWarnings(simulateALAAM(y = emptyLineOutcome, 
                          EdgeList = linePrep$EdgeList, 
                          RowIn = linePrep$RowIn, 
                          degree = linePrep$degree, 
                          covariates = linePrep$covariates, 
                          NumIterations = trials,
                          thinning= 5,
                          theta = zeroTheta,
                          statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                          returnNet = TRUE,
                          canchange = c(1:nrow(lineTest)),
                          DoSave = TRUE))

# save the vector of statistics
zeroSimStats = t(zeroStatSim$statsvec)

# save the sampled edges
zeroSampledEdges = t(zeroStatSim$y)



## Brief inspection of the simulated statistics
summary(zeroSimStats)

# calculate to increase the amount of observed contagion, needs to be done sequentially 
# inverse covariance matrix
zeroInvCov = solve(cov(zeroSimStats))

# amount of changed statistics
smallThetaIncrease = c(0, -15, 0)

# compute the scaled 'increase'
smallScaledDiff = zeroInvCov %*% smallThetaIncrease

# and then the changes in the theta values
smallTheta = as.vector(zeroTheta - smallScaledDiff)

# a small contagion value
smallContSim = simulateALAAM(y = emptyLineOutcome, 
                            EdgeList = linePrep$EdgeList, 
                            RowIn = linePrep$RowIn, 
                            degree = linePrep$degree, 
                            covariates = linePrep$covariates, 
                            NumIterations = trials,
                            thinning= 5,
                            theta = smallTheta,
                            statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                            returnNet = TRUE,
                            canchange = c(1:nrow(lineTest)))
print(smallContSim)

# check how many edges are sampled
table(smallContSim$y)

## do this multiple times to get an approximate range of simulated statistics

  # using the same objects so...
smallStatSim = suppressWarnings(simulateALAAM(y = emptyLineOutcome, 
                          EdgeList = linePrep$EdgeList, 
                          RowIn = linePrep$RowIn, 
                          degree = linePrep$degree, 
                          covariates = linePrep$covariates, 
                          NumIterations = trials,
                          thinning= 5,
                          theta = smallTheta,
                          statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                          returnNet = TRUE,
                          canchange = c(1:nrow(lineTest)),
                          DoSave = TRUE))

# save the vector of statistics
smallSimStats = t(smallStatSim$statsvec) 

# save the sampled edges
smallSampledEdges = t(smallStatSim$y)  
  



# ## tetoing different theta values and the sufficient contagion statisc\
# contSimStats = matrix(data = 0, nrow = trials, ncol = ncol(lineAlaamCovs) + 2)
# 
# tempTheta = smallTheta
# 
# tempInvCov = smallInvCov
# 
# tempStatsVec = c(0, 0, 0)
# 
# tempScaledDiff = smallScaledDiff
# 
# tempOutcome = emptyLineOutcome
# 
# for(trialInd in 1:trials){
#   
#   
#   
#     # using the same objects so...
#   contValueSim = suppressWarnings(simulateALAAM(y = tempOutcome, 
#                             EdgeList = linePrep$EdgeList, 
#                             RowIn = linePrep$RowIn, 
#                             degree = linePrep$degree, 
#                             covariates = linePrep$covariates, 
#                             NumIterations = 1000,
#                             thinning= 5,
#                             theta = as.vector(tempTheta),
#                             statsvec = tempStatsVec,  # getALAAMstats doesn't work when the y is empty (no obs stats)
#                             returnNet = TRUE,
#                             canchange = c(1:nrow(lineTest)),
#                             DoSave = TRUE))
#   
#   # save the vector of statistics
#   contSimStats[trialInd,] = contValueSim$statsvec[,1000] 
#   tempStatsVec = contValueSim$statsvec[,1000]
#   
#   tempOutcome = contValueSim$y[, 1000]
#   
#   # update the covariance matrix
#   tempInvCov = solve(cov(t(contValueSim$statsvec)))
# 
#   # find the scaled difference
#   tempScaledDiff = tempInvCov %*% c(0, -1, 0)
#   
# 
#   
#   
#   # change the theta values
#     tempTheta = tempTheta - tempScaledDiff
# 
# }
# 
# par(mfrow=c(1,2))
# plot(contSimStats[,1])
# plot(contSimStats[,2])

## Brief inspection of the simulated statistics
summary(smallSimStats)

# calculate to increase the amount of observed contagion, needs to be done sequentially 
# inverse covariance matrix
smallInvCov = solve(cov(smallSimStats))

# amount of changed statistics, note that this is in addition to the small theta increase above
largeThetaIncrease = c(0, -25, 0)

# compute the scaled 'increase'
largeScaledDiff = smallInvCov %*% largeThetaIncrease

# and then the changes in the theta values
largeTheta = as.vector(smallTheta - largeScaledDiff)

print(largeTheta)

# a larger contagion value
largeContSim = simulateALAAM(y = emptyLineOutcome, 
                             EdgeList = linePrep$EdgeList, 
                             RowIn = linePrep$RowIn, 
                             degree = linePrep$degree, 
                             covariates = linePrep$covariates, 
                             NumIterations = trials,
                             thinning= 5,
                             theta = largeTheta,
                             statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                             returnNet = TRUE,
                             canchange = c(1:nrow(lineTest)))
print(largeContSim)

# check how many edges are sampled
table(largeContSim$y)

## do this multiple times to get an approximate range of simulated statistics
  
  # using the same objects so...
largeStatSim = suppressWarnings(simulateALAAM(y = emptyLineOutcome, 
                          EdgeList = linePrep$EdgeList, 
                          RowIn = linePrep$RowIn, 
                          degree = linePrep$degree, 
                          covariates = linePrep$covariates, 
                          NumIterations = trials,
                          thinning= 5,
                          theta = largeTheta,
                          statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                          returnNet = TRUE,
                          canchange = c(1:nrow(lineTest)),
                          DoSave = TRUE))

# save the vector of statistics
largeSimStats = t(largeStatSim$statsvec) 

# save the sampled edges
largeSampledEdges = t(largeStatSim$y)


# brief inspection of simulated statistics
summary(largeSimStats)
```


```{r turn into nets}
# code to get their respective edge lists, the contagion parameter is real finicky
zeroContEdgeList = lineTestEdgeList[zeroContSim$y == 1,]
smallContEdgeList = lineTestEdgeList[smallContSim$y == 1,]
largeContEdgeList = lineTestEdgeList[largeContSim$y == 1,]

# edge list to adjMat
emptyExampleMat = matrix(data = 0, nrow = nrow(exampleMat), ncol = ncol(exampleMat))
zeroContMat = emptyExampleMat
smallContMat = emptyExampleMat
largeContMat = emptyExampleMat

# loops one at a time
for(edgeNo in 1:nrow(zeroContEdgeList)){
  
  # grab the sender
  sender = zeroContEdgeList[edgeNo, 1]
  
  # grab the rceiver
  receiver = zeroContEdgeList[edgeNo, 2]
  
  # fill in the empty matrix
  zeroContMat[sender, receiver] = 1
  
  # do the same for the other end because undirected
  zeroContMat[receiver, sender] = 1
}


# but anyways
for(edgeNo in 1:nrow(smallContEdgeList)){
  
  # grab the sender
  sender = smallContEdgeList[edgeNo, 1]
  
  # grab the rceiver
  receiver = smallContEdgeList[edgeNo, 2]
  
  # fill in the empty matrix
  smallContMat[sender, receiver] = 1
  
  # do the same for the other end because undirected
  smallContMat[receiver, sender] = 1
}

for(edgeNo in 1:nrow(largeContEdgeList)){
  
  # grab the sender
  sender = largeContEdgeList[edgeNo, 1]
  
  # grab the rceiver
  receiver = largeContEdgeList[edgeNo, 2]
  
  # fill in the empty matrix
  largeContMat[sender, receiver] = 1
  
  # do the same for the other end because undirected
  largeContMat[receiver, sender] = 1
}

# and plot
gplot(zeroContMat, gmode = "graph", main = "Zero contagion")

gplot(smallContMat, gmode = "graph", main = "Small contagion")

gplot(largeContMat, gmode = "graph", main = "Large contagion")


# now do this for all the simulated networks

# an array because we are gonna have a lot of matrices
zeroSampledArray = array(data = 0, dim = c(nrow(exampleMat), ncol(exampleMat), trials))
smallSampledArray = array(data = 0, dim = c(nrow(exampleMat), ncol(exampleMat), trials))
largeSampledArray = array(data = 0, dim = c(nrow(exampleMat), ncol(exampleMat), trials))

# a loop for all of the simulated sampled edges
for(trialInd in 1:trials){
  
  # turn the line graph into edge lists
  zeroSampledEdgeList = lineTestEdgeList[zeroSampledEdges[trialInd,] == 1,]
  smallSampledEdgeList = lineTestEdgeList[smallSampledEdges[trialInd,] == 1,]
  largeSampledEdgeList = lineTestEdgeList[largeSampledEdges[trialInd,] == 1,]

    # loops one at a time
  for(edgeNo in 1:nrow(zeroSampledEdgeList)){
    
    # grab the sender
    sender = zeroSampledEdgeList[edgeNo, 1]
    
    # grab the rceiver
    receiver = zeroSampledEdgeList[edgeNo, 2]
    
    # fill in the empty matrix
    zeroSampledArray[sender, receiver, trialInd] = 1
    
    # do the same for the other end because undirected
    zeroSampledArray[receiver, sender, trialInd] = 1
  }
  
  
  # but anyways
  for(edgeNo in 1:nrow(smallSampledEdgeList)){
    
    # grab the sender
    sender = smallSampledEdgeList[edgeNo, 1]
    
    # grab the rceiver
    receiver = smallSampledEdgeList[edgeNo, 2]
    
    # fill in the empty matrix
    smallSampledArray[sender, receiver, trialInd] = 1
    
    # do the same for the other end because undirected
    smallSampledArray[receiver, sender, trialInd] = 1
  }
  
  for(edgeNo in 1:nrow(largeSampledEdgeList)){
    
    # grab the sender
    sender = largeSampledEdgeList[edgeNo, 1]
    
    # grab the rceiver
    receiver = largeSampledEdgeList[edgeNo, 2]
    
    # fill in the empty matrix
    largeSampledArray[sender, receiver, trialInd] = 1
    
    # do the same for the other end because undirected
    largeSampledArray[receiver, sender, trialInd] = 1
  }
}

```

## Contagion increase

$$\theta_t = \theta - H(\theta)^{-1}S(\theta)$$
```{r cont manip, eval = F}
# assume ~64% edge sampled as in small cont
startTheta = c(-2, 0.3, 0.1)

# one step to increase contagion values to 0.6
# I need two things-
# actual changes in the theta values
changeTheta = c(0, -0.3, 0)

# covariance matrix for to scale the theta values
# to get this, let's first try with 100 simulations of the same model
trials = 100

# initialising dataframe for sufficient statistics for a model
alaamSuffStats = matrix(data = 0, nrow = trials, ncol = length(startTheta))

# loop to get the statistics
for(i in 1:trials){
  
  # using the same objects so...
  suffStatSim = suppressWarnings(simulateALAAM(y = emptyLineOutcome, 
                            EdgeList = linePrep$EdgeList, 
                            RowIn = linePrep$RowIn, 
                            degree = linePrep$degree, 
                            covariates = linePrep$covariates, 
                            NumIterations = 1000,
                            thinning= 5,
                            theta = c(-2, 0.3, 0.1),
                            statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                            returnNet = TRUE,
                            canchange = c(1:nrow(lineTest))))
  
  # save the vector of statistics
  alaamSuffStats[i,] = suffStatSim$statsvec 
  
  
}

# object type stuff
invCov = solve(cov(alaamSuffStats))

# then (matrix) multply the inverse covariace matrix with the theta change values
scalingFactor = invCov %*% changeTheta

# does this work..?
newTheta = startTheta - scalingFactor

# re-simulate
newThetaSim = simulateALAAM(y = emptyLineOutcome, 
                            EdgeList = linePrep$EdgeList, 
                            RowIn = linePrep$RowIn, 
                            degree = linePrep$degree, 
                            covariates = linePrep$covariates, 
                            NumIterations = 1000,
                            thinning= 5,
                            theta = as.vector(newTheta),
                            statsvec = getALAAMstats(linePrep),  # getALAAMstats doesn't work when the y is empty (no obs stats)
                            returnNet = TRUE,
                            canchange = c(1:nrow(lineTest)))

# print stuff
print(startTheta)

print(scalingFactor)

print(newTheta)

print(smallContSim)

print(newThetaSim)
```


## Calculating metrics

```{r metrics}

### two possible avenues with the 'sampled' adjacency matrices
## Turn into network objects
zeroContNet = as.network(zeroContMat, directed = FALSE)
smallContNet = as.network(smallContMat, direced = FALSE)
largeContNet = as.network(largeContMat, directed = FALSE)


## calculating various metrics
getMetrics = function(net, directed = FALSE){
  
  # fork for directed/undirecited
  mode = "digraph"
  
  if(directed == FALSE){
    mode = "graph"
  } 
  
  # density
  density = gden(net, mode = mode)
  
  # clustering coefficient
  clustCoeff = gtrans(net, mode = mode)
  
  # centralisation
  centralisation = centralization(net, FUN = degree, mode = mode)
  
  # average geodesic
  avgGeod = mean(geodist(net, inf.replace= NA)$gdist, na.rm = T)
  
  # diameter
  diameter = max(geodist(net, inf.replace= NA)$gdist, na.rm = T)
  
  # avg degree
  avgDegree = mean(sna::degree(net, gmode = mode))
  
  # avg betweenness
  avgBetw = mean(betweenness(net, gmode = mode))
  
  # slap them all in a list
  metricList = list(
    density = density,
    clustCoeff = clustCoeff,
    centralisation = centralisation,
    avgGeod = avgGeod,
    diameter = diameter,
    avgDegree = avgDegree,
    avgBetw = avgBetw
  )
  
  # reutrn the metric list
  return(metricList)
}

# apply to the networks
zeroContMetrics = getMetrics(zeroContNet)
smallContMetrics = getMetrics(smallContNet)
largeContMetrics = getMetrics(largeContNet)

# print for now before plotting
print(zeroContMetrics)
print(smallContMetrics)
print(largeContMetrics)

# NOTE: if I wanted to compare to independently sampled dyads, I would need to match the density... right?


## appplying the calculations en masse
# turn them into networkssss
zeroSampledNets = apply(zeroSampledArray, MARGIN = 3, FUN = as.network, directed = FALSE)
smallSampledNets = apply(smallSampledArray, MARGIN = 3, FUN = as.network, directed = FALSE)
largeSampledNets = apply(largeSampledArray, MARGIN = 3, FUN = as.network, directed = FALSE)

# and calculate
zeroMetricList = lapply(zeroSampledNets, FUN = getMetrics)
smallMetricList = lapply(smallSampledNets, FUN = getMetrics)
largeMetricList = lapply(largeSampledNets, FUN = getMetrics)

# getting individual metrics
zeroDensity = sapply(zeroMetricList, function(x){x[["density"]]})
zeroClust = sapply(zeroMetricList, function(x){x[["clustCoeff"]]})
zeroCentr = sapply(zeroMetricList, function(x){x[["centralisation"]]})
zeroAvgGeo = sapply(zeroMetricList, function(x){x[["avgGeod"]]})
zeroDiam = sapply(zeroMetricList, function(x){x[["diameter"]]})
zeroAvgDeg = sapply(zeroMetricList, function(x){x[["avgDegree"]]})
zeroAvgBetw = sapply(zeroMetricList, function(x){x[["avgBetw"]]})

smallDensity = sapply(smallMetricList, function(x){x[["density"]]})
smallClust = sapply(smallMetricList, function(x){x[["clustCoeff"]]})
smallCentr = sapply(smallMetricList, function(x){x[["centralisation"]]})
smallAvgGeo = sapply(smallMetricList, function(x){x[["avgGeod"]]})
smallDiam = sapply(smallMetricList, function(x){x[["diameter"]]})
smallAvgDeg = sapply(smallMetricList, function(x){x[["avgDegree"]]})
smallAvgBetw = sapply(smallMetricList, function(x){x[["avgBetw"]]})

largeDensity = sapply(largeMetricList, function(x){x[["density"]]})
largeClust = sapply(largeMetricList, function(x){x[["clustCoeff"]]})
largeCentr = sapply(largeMetricList, function(x){x[["centralisation"]]})
largeAvgGeo = sapply(largeMetricList, function(x){x[["avgGeod"]]})
largeDiam = sapply(largeMetricList, function(x){x[["diameter"]]})
largeAvgDeg = sapply(largeMetricList, function(x){x[["avgDegree"]]})
largeAvgBetw = sapply(largeMetricList, function(x){x[["avgBetw"]]})


# get the 'true' metric value
trueMetrics = getMetrics(as.network(exampleMat, directed = FALSE))
```


## Independent sampling

Independent sampling of dyads

```{r indep sampling}
# truly independent sampling of the matrix
# since the matrix chosen is undirected, there are only n(n-1)/2 dyads
# I basically need this sampling to sample a triangle, ignoring the diagonal
numberMat = matrix(data = 1:(nrow(exampleMat))^2, ncol = ncol(exampleMat), nrow = nrow(exampleMat))
possibleSampledNumbers = numberMat[upper.tri(numberMat)]

# if I wanted a sampled density that roughly matches the density of the simulated sampled networks, I want to...
# consider density as the % success, work backwards for the actual amount of sampled dyads to match
# the average simulated densities
indepSampledNumbers = replicate(n = trials,
                                    expr = sample(possibleSampledNumbers, size = ((mean(zeroDensity)/trueMetrics$density)* length(possibleSampledNumbers)), replace = FALSE))

# divide by 2 in the sample size because we symmetrise later

# turn these into networks somehow
# for a given set of sampled numbers...,
indepSampledMat = matrix(data = as.numeric(numberMat %in% indepSampledNumbers[, 1]), nrow = nrow(numberMat), ncol = ncol(numberMat))

# symmetrise
indepSampledMat[lower.tri(indepSampledMat)] = t(indepSampledMat)[lower.tri(indepSampledMat)]

# then get the actual matrix
indepAdjMat = indepSampledMat * exampleMat

# an array because we are gonna have a lot of matrices
indepSampledArray = array(data = 0, dim = c(nrow(exampleMat), ncol(exampleMat), trials))



# now do for all
for(trialInd in 1:trials){
  
  # same code as above
  indepSampledMat = matrix(data = as.numeric(numberMat %in% indepSampledNumbers[, trialInd]), nrow = nrow(numberMat), ncol = ncol(numberMat))

  # symmetrise
  indepSampledMat[lower.tri(indepSampledMat)] = t(indepSampledMat)[lower.tri(indepSampledMat)]

  # then get the actual matrix
  indepSampledArray[,,trialInd] = indepSampledMat * exampleMat
}

# turn into networks and calculate metrics
# turn them into networkssss
indepSampledNets = apply(indepSampledArray, MARGIN = 3, FUN = as.network, directed = FALSE)

# and calculate
indepMetricList = lapply(indepSampledNets, FUN = getMetrics)


# getting individual metrics
indepDensity = sapply(indepMetricList, function(x){x[["density"]]})
indepClust = sapply(indepMetricList, function(x){x[["clustCoeff"]]})
indepCentr = sapply(indepMetricList, function(x){x[["centralisation"]]})
indepAvgGeo = sapply(indepMetricList, function(x){x[["avgGeod"]]})
indepDiam = sapply(indepMetricList, function(x){x[["diameter"]]})
indepAvgDeg = sapply(indepMetricList, function(x){x[["avgDegree"]]})
indepAvgBetw = sapply(indepMetricList, function(x){x[["avgBetw"]]})



```



## ERGM Re-estimation

```{r ergm reest}
## re-estimation of some ERGMs and compare to the baseline
# can grab code from miss net reests
# doesn't need to be parallelised to the extent as that script


```


## ALAAM on simulated S

```{r}
### the 'extra credit' for seeing how the markov assumption in dyads translate to the contagion parameter in the ALAAM
# we first need to get an outcome variable (the sampled edge indicator S_l)
# ... first simulate a sampling matrix so that the outcome variable (the sampling indicator) isn't all 1s
# I can use a missNet generator to generate a sampling matrix
# i.e., 75% sampled = 25% missing
source(here("Scripts", "20230811_missNetFunctions.R"))

## Start with a completely independnet example just for computational ease (just sorting out the code first)
randomSampleInd = initMissAdj(n = nrow(exampleMat), propMiss = 0.75, mode = "graph")

# multiply the sampling indicator with the true matrix t get the sampled adjmat
sampledMat = exampleMat * randomSampleInd

## finding which edges remain (in a very roundabout way)
# turn the sampled mat into a line graph
sampledLines = lineGraph(sampledMat, directed = FALSE)

# grab the edge list
sampledEdgeListStr = str_split(rownames(sampledLines), pattern = ",")

# foramat the edge list
sampledEdgeList = data.frame(sender = as.numeric(unlist(lapply(sampledEdgeListStr, FUN = function(x){x[1]}))), 
                             receiver = as.numeric(unlist(lapply(sampledEdgeListStr, FUN = function(x){x[2]}))))

# find which edges overlap
# can't access internet right now so... i'm combining both edge lists and seeing if there are any duplicates
# since the non-duplicates would be the complement to the sampled edge list, they are 0s in the sampled edge indicator (S_L)

combinedEdgeListStr = c(rownames(lineTest), rownames(sampledLines))

# find which ones only appear once
unsampledEdgeStr = names(which(table(combinedEdgeListStr) == 1))

# then do some testing to ensure the two sets are complementary
combinedEdgeTest = c(rownames(sampledLines), unsampledEdgeStr, rownames(lineTest))

# should be 0
sum(table(combinedEdgeTest) != 2)

# therefore the two sets are complements
# so now let's define an outcome variable to be estimated
sampledOutcomeVar = rep(1, nrow(lineTest))
sampledOutcomeVar[rownames(lineTest) %in% unsampledEdgeStr] = 0

# this is then technically ready to estimate
### Estimation model for the ALAAM here.

```

## Snowball simulation

```{r snowsim}
### Simulation of a snowball sample mechanism
# with the london gangs as the example
# let's say we have a wave size of between 15 for each wave
waveSize = 15

possibleNodes = 1:nrow(exampleMat)

# sample the seed set
seedSet = sample(x = possibleNodes, size = waveSize, replace = FALSE)

# initialise an empty matrix
snowMat = matrix(data = 0, nrow = length(possibleNodes), ncol = length(possibleNodes))

# then sample the ones that have been sampled
snowMat[seedSet,] = exampleMat[seedSet,]

# symmetrising because undirected
snowMat[, seedSet] = exampleMat[, seedSet]

# plot it
gplot(snowMat, gmode = "graph", main = "Seed")

# then prioritise sampling nodes that are incident on the already sampled nodes
seedEdgeList = which(snowMat==1, arr.ind = TRUE)

# then check which columns are incident to the seed set
possibleWave1 = setdiff(as.numeric(names(table(seedEdgeList))), seedSet)

# so sample wave 1
wave1Set = sample(x = possibleWave1, size = waveSize, replace = FALSE)

# sample wave 1
snowMat[wave1Set,] = exampleMat[wave1Set,]
snowMat[,wave1Set] = exampleMat[,wave1Set]

# plot it
gplot(snowMat, gmode = "graph", main = "Wave 1")

# check which ones can be sampled again
wave1EdgeList = which(snowMat==1, arr.ind = TRUE)

# then check which columns are incident to the seed set
possibleWave2 = setdiff(as.numeric(names(table(wave1EdgeList))), c(seedSet, wave1Set))

# keep going
# so sample wave 2
wave2Set = possibleWave2

if( length(possibleWave2) > waveSize){
  wave2Set = sample(x = possibleWave2, size = waveSize, replace = FALSE)
}


# sample wave 2
snowMat[wave2Set,] = exampleMat[wave2Set,]
snowMat[,wave2Set] = exampleMat[,wave2Set]

# plot it
gplot(snowMat, gmode = "graph", main = "Wave 2")

# check which ones can be sampled again
wave2EdgeList = which(snowMat==1, arr.ind = TRUE)

# then check which columns are incident to the seed set
possibleWave3 = setdiff(as.numeric(names(table(wave2EdgeList))), c(seedSet, wave1Set, wave2Set))

# wave 3 migth not happen depending on which nodes are sampled since some have fairly high degree
if(length(possibleWave3) > 0){
# so sample wave 3, no randomised sampling here because there are not enough nodes
wave3Set = possibleWave3

# sample wave 3
snowMat[wave3Set,] = exampleMat[wave3Set,]
snowMat[,wave3Set] = exampleMat[,wave3Set]

# plot it
gplot(snowMat, gmode = "graph", main = "Wave 3")

# check which ones can be sampled again
wave3EdgeList = which(snowMat==1, arr.ind = TRUE)
}


```

Use node colour to show which nodes have been sampled vs. not sampled? Also maybe mess with starting with a smaller matrix before adding rows and columns to it.


## Plotting code

```{r plotcode}
# package
library(ggplot2)


# density
densityPlotData = data.frame(density = c(indepDensity, zeroDensity, smallDensity, largeDensity), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

densityPlot = ggplot( data = densityPlotData,
                    aes( x = density, col = model, fill = model)) + 
             xlab("Density") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$density, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Density") + 
             theme_classic()

densityPlot

# Clustering coefficient
clustPlotData = data.frame(clust = c(indepClust, zeroClust, smallClust, largeClust), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

clustPlot = ggplot( data = clustPlotData,
                    aes( x = clust, col = model, fill = model)) + 
             xlab("Clustering coefficient") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$clustCoeff, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Clustering coefficient") + 
             theme_classic()

clustPlot


# Centralisation
centrPlotData = data.frame(centr = c(indepCentr, zeroCentr, smallCentr, largeCentr), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

centrPlot = ggplot( data = centrPlotData,
                    aes( x = centr, col = model, fill = model)) + 
             xlab("Centralisation") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$centralisation, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Centralisation") + 
             theme_classic()

centrPlot


# Avg geod
avgGeoPlotData = data.frame(avgGeo = c(indepAvgGeo, zeroAvgGeo, smallAvgGeo, largeAvgGeo), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

avgGeoPlot = ggplot( data = avgGeoPlotData,
                    aes( x = avgGeo, col = model, fill = model)) + 
             xlab("Average geodesic") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$avgGeod, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Average geodesic") + 
             theme_classic()

avgGeoPlot


# Diameter
diamPlotData = data.frame(diam = c(indepDiam, zeroDiam, smallDiam, largeDiam), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

diamPlot = ggplot( data = diamPlotData,
                    aes( x = diam, col = model, fill = model)) + 
             xlab("Diameter") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$diameter, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Diameter") + 
             theme_classic()

diamPlot

# Avg degree
avgDegPlotData = data.frame(avgDeg = c(indepAvgDeg, zeroAvgDeg, smallAvgDeg, largeAvgDeg), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

avgDegPlot = ggplot( data = avgDegPlotData,
                    aes( x = avgDeg, col = model, fill = model)) + 
             xlab("Average degree") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$avgDegree, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Average degree") + 
             theme_classic()

avgDegPlot

# betw
avgBetwPlotData = data.frame(avgBetw = c(indepAvgBetw, zeroAvgBetw, smallAvgBetw, largeAvgBetw), 
                            model = factor(c(rep("Indep", trials), rep("ZeroCont", trials), rep("SmallCont", trials), rep("LargeCont", trials)),
                                           levels = c("Indep", "ZeroCont", "SmallCont", "LargeCont")),
                            runs = rep(1:trials, 4))

avgBetwPlot = ggplot( data = avgBetwPlotData,
                    aes( x = avgBetw, col = model, fill = model)) + 
             xlab("Average betweenness centrality") + 
             ylab("Frequency") +
             geom_vline(xintercept = trueMetrics$avgBetw, col = "darkblue") + 
             geom_density(alpha = 0.4) +
             ggtitle("Diagnostics - Average betweenness centrality") + 
             theme_classic()

avgBetwPlot
```

## Some more figs

```{r line graph fig}
# colouring nodes manually... kinda.
coord = gplot(lineTest, gmode = "graph")

lineNodeCol = rep("orange", nrow(lineTest))
lineNodeCol[largeContSim$y == 1] = "blue"

gplot(lineTest, gmode = "graph", vertex.col = lineNodeCol, coord = coord, main = "Sampled line graph")


coord = gplot(exampleMat, gmode = "graph")

edgeCol = rep("orange", nrow(lineTest))
edgeCol[largeContSim$y ==1] = "blue"

gplot(exampleMat, gmode = "graph", edge.col = edgeCol, coord = coord, main = "Sampled adjacency matrix")


```


