---
title: "20230616_sunbeltSimulations"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goals of this document

I need to generate various missingness models:

-   Independent tie variables with a homogenous missingness probability
-   A Markov model that isn't conditional on the network
-   A Markov model that IS conditional on the network
-   The specified ERGM with a positive entrainment effect (d_ij is affected by x_ij), degree (x_i+ + x\_+j), some markov dependence (2star and triangles)

All with approximately the same proportion of missingness (arbitrarily \~40%ish??)

-   Choose an extant dataset (one of the UCINet ones)
-   Converge a model on said dataset
-   Deplete the model with the missingness models
-   Evalute the effects of the missingness



**general update:** refine these simulations into functional forms. make sure these work with differing adjmats (e.g., take multiple datasets from the ucinet database and make it so I can switch the chosen adjmat with the code adapting to the changing networks.)


## Estimating a model on extant data

```{r read in bombing data}
# packages
library(here)
library(ergm)
library(sna)
library(network)

# as taken from UCINET (17 Nov Greek Bombings)
greeceBombs = as.matrix(read.csv(file = here("Data", "17Nov Greece Bombing", "17NOV_GREECE_19751984.csv"), header = T, row.names = "X"))

# symmetrising column and row names because isSymmetric checks this
colnames(greeceBombs) = rownames(greeceBombs)

# add in the missing tie, ONLY FOR 19952002, the other two versions already have this as 1.
greeceBombs[4,18] = 1

# making sure it's an undirected network
print(paste("Check on whether the network is undirected:", isSymmetric(greeceBombs)))

# brief inspection
# density
print(paste("Density:", round(mean(greeceBombs), 3)))

par(mfrow = c(1,2))

# plot network
gplot(greeceBombs,
      gmode = "graph",
      edge.col = "grey",
     # vertex.cex = sna::degree(greeceBombs)*0.2,
      main = "Nov 17 bombing network")

# check degree distribution
plot(table(colSums(greeceBombs)), type = "h", main = "Degree distribution", xlab = "Degree", ylab = "Frequency")

# turn into a network and estimate
bombNet = as.network(greeceBombs, directed = FALSE)

# model specification
trueModel = bombNet ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE)

# run ergm
n17res = ergm(trueModel, 
     control = control.ergm(init = c(-4.38, 0.48, 1.51), MCMC.burnin = 5024, MCMC.interval=5024))

# maybe try updating the  ergm package

# summary
summary(n17res)
```


## Generating missingness

### Simulated toy network

```{r simuNet}
# generating a simulated undirected network as X
# set number of nodes, choosing 30 arbitrarily
n = 18

# using a uniform dist
simMat = matrix(data = 0, nrow = n, ncol = n)

# randomly generate values for all nonzero values (i.e., all off-diagonal elements) 
# take only one triangle
simMat[upper.tri(simMat)] = runif((n*(n-1))/2)

# and symmetrise
simMat[lower.tri(simMat)] = t(simMat)[lower.tri(simMat)]

# use some threshold (this would be the density)
threshold = 0.25

# all values above the threshold are not ties
simMat[simMat > threshold] = 0

# all nonzero elements are then ties
simMat[simMat != 0] = 1

# how to approach this symmetrically..?
```

### 'Brute forcing' starting parameters

```{r start paras, eval = F}
# randomly choosing ergm parameter values is driving me nuts
# so I'll just randomly generate a network with the approximate amount of missingness
# and estimate a model on it for coefficients to use for simulation

# turn the previously simulated random network with the specified threshold as an undirected network object
simNet = as.network(simMat, directed = FALSE)

# degree as a node covariate
n17degree = rowSums(greeceBombs)

# slap it on the network object
simNet %v% 'degree' = n17degree

# compare with a degree dyadcov
sentTies = matrix(rep(rowSums(greeceBombs), nrow(greeceBombs)), nrow = nrow(greeceBombs), ncol = ncol(greeceBombs))
receivedTies = matrix(rep(colSums(greeceBombs), ncol(greeceBombs)), nrow = nrow(greeceBombs), ncol = ncol(greeceBombs), byrow = T)

# sum them up for an edge covariate weighed by degree
degreeCov = sentTies + receivedTies

# diag is 0 because adjmat
diag(degreeCov) = 0

# specify the model
simModel = simNet ~ edges + kstar(2) + triangle + dyadcov(greeceBombs) + dyadcov(degreeCov)

# estimate it
simRes = ergm(simModel,
              control = control.ergm(MCMC.burnin = 20000,
                                     MCMC.interval = 20000,
                                     init.method = "CD"))

# check it
summary(simRes)

```



### Independent tie variables

```{r independent D}
## taking some old code 

# degrade net function from previous script
indepMiss <- function(adjMat, propMiss, directed = FALSE){
  
  ## indepMiss(adjMat, propMiss, directed) takes a graph and replaces the observed graph ties with missing 
  ## values(NA). This function does not handle actor non-response as it only works off the observed
  ## network ties. Works with undirected networks.
  ##
  ## Input:
  ## - adjMat:    An adjacency matrix describing a graph. There shouldn't
  ##             be any missing values in this adjacency matrix yet.
  ##             Should still work if there were though. I think.
  ## - propMiss: A numeric value to indicate the proportion of missingness
  ##             that will be imposed on the observed network.
  ##             Is bounded between 0 and 1.
  ## - directed: A logical value to indicate if it's a directed or
  ##             undirected network. Default is set to undirected.
  ##
  ## Output: 
  ## - A degraded network with missing ties where observed ties once were.
  ##   Note that it only handles item non-response for now. Given the inputs,
  ##   the missing values would be ~'propMiss'% of the observed tie variables in 'graph'.
  
  ## spit out an error if the directed argument is misspecified
  if(directed != TRUE & !isSymmetric(adjMat)){
    stop("The undirected network doesn't have a symmetric matrix")
  }
  
  ## spit out an error if the proportion of missingness exceeds bounds
  if(propMiss > 1 | propMiss < 0){
    stop("The proportion of missingness exceeds bounds")
  }
  
  # grab the number of nodes
  n = nrow(adjMat)
  
  # make an n x n matrix containing randomly generated values between 0 and 1
  missThresh = matrix(data = runif(n^2, min = 0, max = 1),
                      nrow = n,
                      ncol = n)
  
  # set diagonal to 0 for the dircted network
  diag(missThresh) = 0
  
  # branch for undirected network
  if( directed == FALSE ){
    
    # make a matrix
    missThresh = matrix(data = 0, nrow = n, ncol = n)
    
    # take only one triangle
    missThresh[upper.tri(missThresh)] = runif((n*(n-1))/2)

    # and symmetrise
    missThresh[lower.tri(missThresh)] = t(missThresh)[lower.tri(missThresh)]
  }
     
  # index which of the ties are going to be missing
  missTies = missThresh <= propMiss
  
  # copy the graph to punch holes in it
  degradedGraph = adjMat
    
  # punch holes
  degradedGraph[missTies] = NA
  
  # diagonal is always fixed to 0, this is an artefact of the way missingness is generated
  diag(degradedGraph) = 0
  
  # return the degraded graph
  return(degradedGraph)
}


## Test run of the function above
indepMissTrial = indepMiss(adjMat = greeceBombs, propMiss = 0.3, directed = FALSE)

# grabbing the D matrix
indepMissMat = 1 * is.na(indepMissTrial) 

## Seems good enough
```

### Markov model not conditional on the network

```{r mrkv model uncond}
## The network the ergm's supposed to be 'modelling'
## But since we're using it strictly for simulation purposes, we're starting empty
missMat = matrix(data = 0, nrow = n, ncol = n)

# format as network object
missNet = as.network(missMat, directed = FALSE)

## specify an ergm, unconditional to the actual data
UncondMrkv = missNet ~ edges + kstar(2) + triangle

```

```{r uncondmrkv simulate}
## choose some parameter values
chosenCoefUM = c(-2.12,
                 0.17,
              #   -0.3, three stars are hard
                 -0.3)

# generate simulated networks
simMissNetStatsUM <- simulate(UncondMrkv ,
                        coef = chosenCoefUM, # I think these parameters should yield non-degenerate models
                        nsim = 1000 ,# how many samples to pick up
                        control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024),#for estimate it is 'control'
                        output='stats')


# trace plots to see how the parameter values are doing
par(mfrow = c(2,2))
plot(ts(simMissNetStatsUM[,"edges"]), ylab = "Edges", xlab = paste("Par value =", chosenCoefUM[1]))
plot(ts(simMissNetStatsUM[,"kstar2"]), ylab = "2-stars", xlab = paste("Par value =", chosenCoefUM[2]))
# plot(ts(simMissNetStatsUM[,"kstar3"]), ylab = "3-stars", xlab = paste("Par value =", chosenCoefUM[3]))
plot(ts(simMissNetStatsUM[,3]), ylab = "Triangle", xlab = paste("Par value =", chosenCoefUM[3]))
mtext("Unconditional Markov model",
      side = 3,
      line = -2,
      outer = TRUE)

# take some draws
simMissNetsUM <- simulate(UncondMrkv ,
                        coef = chosenCoefUM, # I think these parameters should yield non-degenerate models
                        nsim = 1000 ,# how many samples to pick up
                        control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024))#for estimate it is 'control'

```

### Markov model conditional on the network

```{r mrkv model cond}

## specify an ergm, conditional to the actual data with an entrainment effect
condMrkv = missNet ~ edges + kstar(2) + triangle + dyadcov(greeceBombs)

## choose some parameter values
chosenCoefCM = c(-2.12,
                 0.17,
                -0.28,
                 -0.4)

# generate simulated networks
simMissNetStatsCM <- simulate(condMrkv ,
                        coef = chosenCoefCM, # I think these parameters should yield non-degenerate models
                        nsim = 1000 ,# how many samples to pick up
                        control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024),#for estimate it is 'control'
                        output='stats')

# trace plots to see how the parameter values are doing
par(mfrow = c(2,2))
plot(ts(simMissNetStatsCM[,"edges"]), ylab = "Edges", xlab = paste("Par value =", chosenCoefCM[1]))
plot(ts(simMissNetStatsCM[,"kstar2"]), ylab = "2-stars", xlab = paste("Par value =", chosenCoefCM[2]))
plot(ts(simMissNetStatsCM[,"triangle"]), ylab = "Triangle", xlab = paste("Par value =", chosenCoefCM[3]))
plot(ts(simMissNetStatsCM[,"dyadcov.greeceBombs"]), ylab = "Entrainment", xlab = paste("Par value =", chosenCoefCM[4]))

mtext("Conditional Markov model",
      side = 3,
      line = -2,
      outer = TRUE)

# take some draws
simMissNetsCM <- simulate(condMrkv ,
                        coef = chosenCoefCM, # I think these parameters should yield non-degenerate models
                        nsim = 1000 ,# how many samples to pick up
                        control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024)) #for estimate it is 'control'
```

### ERGM

```{r ergmtime baby}
## Say a degree covariate with the actual data
## edge covariate for the sum of degrees
# a cute piece of vectorised code to give each tie variable a weight based on the sender and receiver
sentTies = matrix(rep(rowSums(greeceBombs), nrow(greeceBombs)), nrow = nrow(greeceBombs), ncol = ncol(greeceBombs))
receivedTies = matrix(rep(colSums(greeceBombs), ncol(greeceBombs)), nrow = nrow(greeceBombs), ncol = ncol(greeceBombs), byrow = T)

# sum them up for an edge covariate weighed by degree
degreeCov = sentTies + receivedTies

# diag is 0 because adjmat
diag(degreeCov) = 0

# another way to do the above is just using the node's degree as a degree covariate
n17degree = rowSums(greeceBombs)

## slap it on the network object
missNet %v% 'degree' = n17degree


## adding in the degree effect
ergmMod = missNet ~ edges + kstar(2) + triangle +  dyadcov(greeceBombs) + nodecov('degree')

## choose some parameter values
chosenCoefERGM = c(-2.3,
                 0.17,
                -0.28,
                 -0.2,
                 0.04)

# generate simulated networks
simMissNetStatsERGM <- simulate(ergmMod ,
                        coef = chosenCoefERGM, # I think these parameters should yield non-degenerate models
                        nsim = 1000 ,# how many samples to pick up
                        control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024),#for estimate it is 'control'
                        output='stats')

# trace plots to see how the parameter values are doing
par(mfrow = c(2,3))
plot(ts(simMissNetStatsERGM[,"edges"]), ylab = "Edges", xlab = paste("Par value =", chosenCoefERGM[1]))
plot(ts(simMissNetStatsERGM[,"kstar2"]), ylab = "2-stars", xlab = paste("Par value =", chosenCoefERGM[2]))
plot(ts(simMissNetStatsERGM[,"triangle"]), ylab = "Triangle", xlab = paste("Par value =", chosenCoefERGM[3]))
plot(ts(simMissNetStatsERGM[,"dyadcov.greeceBombs"]), ylab = "Entrainment", xlab = paste("Par value =", chosenCoefERGM[4]))
plot(ts(simMissNetStatsERGM[,"nodecov.degree"]), ylab = "Degree nodecov", xlab = paste("Par value =", chosenCoefERGM[5]))

mtext("Full ERGM",
      side = 3,
      line = -2,
      outer = TRUE)

## Take some draws
simMissNetsERGM <- simulate(ergmMod ,
                            coef = chosenCoefERGM, # I think these parameters should yield non-degenerate models
                            nsim = 1000 ,# how many samples to pick up
                            control=control.simulate.formula(MCMC.burnin=1024,MCMC.interval=1024))#for estimate it is 'control'

```


## Depleting the network with different models

### Choosing missingness matrices

```{r choosing missingns}
# a loop to draw some (missingness) networks with over 25% missing
# initialise
goodCount = 0

# a while loop becuase i'm spicy
while(goodCount < 4){
  
  # randomly sample an index
  index = sample(1:1000, 1)
  
  # differently for the independent model
  # use the function
  indepMissNet = indepMiss(adjMat = greeceBombs, propMiss = 0.25, directed = FALSE)
  
  # take a network out
  chosenIndep = 1 * is.na(indepMissNet)
  chosenMissNetUM = simMissNetsUM[index]
  chosenMissNetCM = simMissNetsCM[index]
  chosenMissNetERGM = simMissNetsERGM[index]

  # grab the edge counts
  edgeCounts = c(sum(chosenIndep)/2, 
                 network.edgecount(chosenMissNetUM[[1]]), 
                 network.edgecount(chosenMissNetCM[[1]]), 
                 network.edgecount(chosenMissNetERGM[[1]]))
  
  # check if in range
  over40 = edgeCounts >= 40
  under49 = edgeCounts < 49
  edgeRange = over40 & under49
  
  # and average it
  goodCount = sum(edgeRange)
}

# turn them all into matrix objects
chosenMissMatUM = as.matrix(chosenMissNetUM[[1]])
chosenMissMatCM = as.matrix(chosenMissNetCM[[1]])
chosenMissMatERGM = as.matrix(chosenMissNetERGM[[1]])


```


## Reestimating the ERGMs

### Peter

```{r reeeedo peter}
# a loop to draw some (missingness) networks with over 25% missing
# initialise
goodCount = 0

# a while loop becuase i'm spicy
while(goodCount < 4){
  
  # randomly sample an index
  index = sample(1:1000, 1)
  
  # differently for the independent model
  # use the function
  indepMissNet = indepMiss(adjMat = greeceBombs, propMiss = 0.25, directed = FALSE)
  
  # take a network out
  chosenIndep = 1 * is.na(indepMissNet)
  chosenMissNetUM = simMissNetsUM[index]
  chosenMissNetCM = simMissNetsCM[index]
  chosenMissNetERGM = simMissNetsERGM[index]

  # grab the edge counts
  edgeCounts = c(sum(chosenIndep)/2, 
                 network.edgecount(chosenMissNetUM[[1]]), 
                 network.edgecount(chosenMissNetCM[[1]]), 
                 network.edgecount(chosenMissNetERGM[[1]]))
  
  # check if in range
  over40 = edgeCounts >= 40
  under49 = edgeCounts < 49
  edgeRange = over40 & under49
  
  # and average it
  goodCount = sum(edgeRange)
}

# turn them all into matrix objects
chosenMissMatUM = as.matrix(chosenMissNetUM[[1]])
chosenMissMatCM = as.matrix(chosenMissNetCM[[1]])
chosenMissMatERGM = as.matrix(chosenMissNetERGM[[1]])


# copy over the adjacency matrix
greeceBombsMissIndep = greeceBombs
greeceBombsMissUM = greeceBombs
greeceBombsMissCM = greeceBombs
greeceBombsMissERGM = greeceBombs

# Now we're actually depleting the network
greeceBombsMissIndep[chosenIndep == 1] = NA
greeceBombsMissUM[chosenMissMatUM == 1] = NA
greeceBombsMissCM[chosenMissMatCM == 1] = NA
greeceBombsMissERGM[chosenMissMatERGM == 1] = NA

# turn into networks again
bombNetMissIndep = as.network(greeceBombsMissIndep, directed = FALSE)
bombNetMissUM = as.network(greeceBombsMissUM, directed = FALSE)
bombNetMissCM = as.network(greeceBombsMissCM, directed = FALSE)
bombNetMissERGM = as.network(greeceBombsMissERGM, directed = FALSE)

# models to be reestimated
bombNetMissIndepModel = bombNetMissIndep ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissUMModel = bombNetMissUM ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissCMModel = bombNetMissCM ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissERGMModel = bombNetMissERGM ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 

# reeeeeestimations
depletedMissIndep = ergm(bombNetMissIndepModel,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissUM = ergm(bombNetMissUMModel,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissCM = ergm(bombNetMissCMModel,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissERGM = ergm(bombNetMissERGMModel,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))

## Note: screw reestimations, just read in the ones I've saved.

# copy over the adjacency matrix
greeceBombsMissIndepTodd = greeceBombs
greeceBombsMissUMTodd = greeceBombs
greeceBombsMissCMTodd = greeceBombs
greeceBombsMissERGMTodd = greeceBombs

# Now we're actually depleting the network
greeceBombsMissIndepTodd[chosenIndep == 1] = 0
greeceBombsMissUMTodd[chosenMissMatUM == 1] = 0
greeceBombsMissCMTodd[chosenMissMatCM == 1] = 0
greeceBombsMissERGMTodd[chosenMissMatERGM == 1] = 0

# turn into networks again
bombNetMissIndepTodd = as.network(greeceBombsMissIndepTodd, directed = FALSE)
bombNetMissUMTodd = as.network(greeceBombsMissUMTodd, directed = FALSE)
bombNetMissCMTodd = as.network(greeceBombsMissCMTodd, directed = FALSE)
bombNetMissERGMTodd = as.network(greeceBombsMissERGMTodd, directed = FALSE)

# models to be reestimated
bombNetMissIndepModelTodd = bombNetMissIndepTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissUMModelTodd = bombNetMissUMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissCMModelTodd = bombNetMissCMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissERGMModelTodd = bombNetMissERGMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 

# reeeeeestimations
depletedMissIndepTodd = ergm(bombNetMissIndepModelTodd,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissUMTodd = ergm(bombNetMissUMModelTodd,
             control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissCMTodd = ergm(bombNetMissCMModelTodd,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))
depletedMissERGMTodd = ergm(bombNetMissERGMModelTodd,
              control = control.ergm(init = c(-1.407, 
    -1.1974, 2.189), MCMC.interval = 5024))


```

### Todd

```{r todd}
# copy over the adjacency matrix
greeceBombsMissIndepTodd = greeceBombs
greeceBombsMissUMTodd = greeceBombs
greeceBombsMissCMTodd = greeceBombs
greeceBombsMissERGMTodd = greeceBombs

# Now we're actually depleting the network
greeceBombsMissIndepTodd[chosenIndep == 1] = 0
greeceBombsMissUMTodd[chosenMissMatUM == 1] = 0
greeceBombsMissCMTodd[chosenMissMatCM == 1] = 0
greeceBombsMissERGMTodd[chosenMissMatERGM == 1] = 0

# turn into networks again
bombNetMissIndepTodd = as.network(greeceBombsMissIndepTodd, directed = FALSE)
bombNetMissUMTodd = as.network(greeceBombsMissUMTodd, directed = FALSE)
bombNetMissCMTodd = as.network(greeceBombsMissCMTodd, directed = FALSE)
bombNetMissERGMTodd = as.network(greeceBombsMissERGMTodd, directed = FALSE)

# models to be reestimated
bombNetMissIndepModelTodd = bombNetMissIndepTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissUMModelTodd = bombNetMissUMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissCMModelTodd = bombNetMissCMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 
bombNetMissERGMModelTodd = bombNetMissERGMTodd ~ edges + gwdegree(decay = log(2), fixed = TRUE) + gwesp(decay = log(2), fixed = TRUE) 

# reeeeeestimations
# depletedMissIndepTodd = ergm(bombNetMissIndepModelTodd,
#               control = control.ergm( #init.method = "CD",
#                                      MCMC.burnin = 10000,
#                                      MCMC.interval = 10000))
# depletedMissUMTodd = ergm(bombNetMissUMModelTodd,
#               control = control.ergm( #init.method = "CD",
#                                      MCMC.burnin = 10000,
#                                      MCMC.interval = 10000))
depletedMissCMTodd = ergm(bombNetMissCMModelTodd,
              control = control.ergm( #init.method = "CD",
                                     MCMC.burnin = 10000,
                                     MCMC.interval = 10000))
# depletedMissERGMTodd = ergm(bombNetMissERGMModelTodd,
#               control = control.ergm( #init.method = "CD",
#                                      MCMC.burnin = 10000,
#                                      MCMC.interval = 10000))

```



### Evaluating the depleted networks

Metrics to check:
density
centrality (degree, betweenness)
mean geodesic
avg degree
centralisation

```{r metrics for depleted nets}
# 

```


