---
title: "20250308_statnetSimCheck"
author: "Jon Januar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this document is to inspect what the most consistent simulated networks through some 'basic' statnet functionality. This is an inspection to figure out some ergm squared sampler stability.

A bernoulli model will do because 


## Loading stuff

```{r load}
# checking statnet simulations
library(ergm)
library(here)

# some network
data("faux.mesa.high")
fmhModel = faux.mesa.high ~ edges + nodematch("Grade")

fmhFit <- ergm(fmhModel)

# check simulation stability
fmhSim = simulate(fmhModel, 
                  nsim = 1,
                  coef = c(-6.034, 2.831),
                  control = snctrl(MCMC.burnin = 20000, MCMC.interval = 20000))

fmhTarget = summary(fmhModel)
```


## Running sims

```{r runsim}

# a couple of conditions, 100 sim nets ea to check stability, 
iters = 300

# since the interval affects the sampled networks i'm doing this crudely and looping this.
# default options
fmhSimDef = list()

for(index in 1:iters){
  fmhSimDef[[index]] = simulate(fmhModel, 
                                nsim = 1,
                                coef = c(-6.034, 2.831))
}

# 20000 burnin
fmhSimBrn = list()

for(index in 1:iters){
  fmhSimBrn[[index]] = simulate(fmhModel, 
                                nsim = 1,
                                coef = c(-6.034, 2.831),
                                control = snctrl(MCMC.burnin = 20000))
}


# 20000 burnin and interval
fmhSimBrnInt = list()

for(index in 1:iters){
  fmhSimBrnInt[[index]] = simulate(fmhModel, 
                                  nsim = 1,
                                  coef = c(-6.034, 2.831),
                                  control = snctrl(MCMC.burnin = 20000, MCMC.interval = 20000))
}



# 20000 burnin and interval, 2 simulated networks and take the second one
fmhSimBrnInt2 = list()

for(index in 1:iters){
 tempNetList = simulate(fmhModel, 
                        nsim = 2,
                        coef = c(-6.034, 2.831),
                        control = snctrl(MCMC.burnin = 20000, MCMC.interval = 20000))
 
 fmhSimBrnInt2[[index]] = tempNetList[[2]]
}

```

## Checking simulations

```{r grabstats}
# check the statistics
defStats = lapply(fmhSimDef, FUN = function(x){summary(x~edges + nodematch("Grade"))})
brnStats = lapply(fmhSimBrn, FUN = function(x){summary(x~edges + nodematch("Grade"))})
brnIntStats = lapply(fmhSimBrnInt, FUN = function(x){summary(x~edges + nodematch("Grade"))})
brnInt2Stats = lapply(fmhSimBrnInt2, FUN = function(x){summary(x~edges + nodematch("Grade"))})

# grab the simulated statistics
grabEdges = function(statList){
  unlist(lapply(statList, FUN = function(x){x[1]}))
}

grabGrade = function(statList){
  unlist(lapply(statList, FUN = function(x){x[2]}))
}

# and do this for all the lists
defEdges = grabEdges(defStats)
brnEdges = grabEdges(brnStats)
brnIntEdges = grabEdges(brnIntStats)
brnInt2Edges = grabEdges(brnInt2Stats)

# and grade
defGrade = grabGrade(defStats)
brnGrade = grabGrade(brnStats)
brnIntGrade = grabGrade(brnIntStats)
brnInt2Grade = grabGrade(brnInt2Stats)

```


```{r plot}
# plot and check
plot(density(defEdges), main = paste("default edges, sd =", sd(defEdges)))
abline(v = fmhTarget[1], col = "red")

plot(density(brnEdges), main = paste("brn edges, sd =", sd(brnEdges)))
abline(v = fmhTarget[1], col = "red")

plot(density(brnIntEdges), main = paste("brnInt edges, sd =", sd(brnIntEdges)))
abline(v = fmhTarget[1], col = "red")

plot(density(brnInt2Edges), main = paste("brnInt2 edges, sd =", sd(brnInt2Edges)))
abline(v = fmhTarget[1], col = "red")

# grade stats
plot(density(defGrade), main = paste("default Grade, sd =", sd(defGrade)))
abline(v = fmhTarget[2], col = "red")

plot(density(brnGrade), main = paste("brn Grade, sd =", sd(brnGrade)))
abline(v = fmhTarget[2], col = "red")

plot(density(brnIntGrade), main = paste("brnInt Grade, sd =", sd(brnIntGrade)))
abline(v = fmhTarget[2], col = "red")

plot(density(brnInt2Grade), main = paste("brnInt2 Grade, sd =", sd(brnInt2Grade)))
abline(v = fmhTarget[2], col = "red")

```


## The same with an endogenous model

Since this functionality's used for the auxiliary networks in the chaos sampler...

```{r endosetup}
# grab data, good ol london gangs
# Load in some dataset
load(here("Data", "20231006_missNetsEnMasse.RData"))

# London gangs since it's an easy dataset with some attributes
trueAdj = adjMatList[[6]]

# get the true statistics for the given estimation model for reference
trueNet = as.network(trueAdj, directed = FALSE)
trueNet %v% 'Age' = scale(londonGangsAtt$Age)[,1]

# get the 'true' values
trueModel = trueNet ~ edges +
  gwdegree(0.69, fixed = TRUE) +
  gwesp(0.69, fixed = TRUE) +
  nodecov("Age") +
  absdiff("Age")

trueStats = as.numeric(summary(trueModel))

print(trueStats)


# for future purposes, the coefs are c(-4.409, 0.92919, 1.386, 0.163, -0.489)
# cheat by using the natural mle parameters of the complete network to get initial parameters
trueRes = ergm(trueModel,
               control = control.ergm(init = c(-4.409, 0.92919, 1.386, 0.163, -0.489),
                                      MCMC.burnin = 20000, 
                                      MCMC.interval = 20000))

```

## Gangs sims

```{r runsim}
# a couple of conditions, 100 sim nets ea to check stability, 
iters = 300

# since the interval affects the sampled networks i'm doing this crudely and looping this.
# default options
gangSimDef = list()

for(index in 1:iters){
  gangSimDef[[index]] = simulate(trueModel, 
                                nsim = 1,
                                coef = c(-4.409, 0.92919, 1.386, 0.163, -0.489))
}

# 20000 burnin
gangSimBrn = list()

for(index in 1:iters){
  gangSimBrn[[index]] = simulate(trueModel, 
                                nsim = 1,
                                coef = c(-4.409, 0.92919, 1.386, 0.163, -0.489),
                                control = snctrl(MCMC.burnin = 20000))
}


# 20000 burnin and interval
gangSimBrnInt = list()

for(index in 1:iters){
  gangSimBrnInt[[index]] = simulate(trueModel, 
                                  nsim = 1,
                                  coef = c(-4.409, 0.92919, 1.386, 0.163, -0.489),
                                  control = snctrl(MCMC.burnin = 20000, MCMC.interval = 20000))
}



# 20000 burnin and interval, 2 simulated networks and take the second one
gangSimBrnInt2 = list()

for(index in 1:iters){
 tempNetList = simulate(trueModel, 
                        nsim = 2,
                        coef = c(-4.409, 0.92919, 1.386, 0.163, -0.489),
                        control = snctrl(MCMC.burnin = 20000, MCMC.interval = 20000))
 
 gangSimBrnInt2[[index]] = tempNetList[[2]]
}

```

## Gangs check

```{r grabstats}
# check the statistics
defStats = lapply(gangSimDef, FUN = function(x){summary(x~edges +
  gwdegree(0.69, fixed = TRUE) +
  gwesp(0.69, fixed = TRUE) +
  nodecov("Age") +
  absdiff("Age"))})
brnStats = lapply(gangSimBrn, FUN = function(x){summary(x~edges +
  gwdegree(0.69, fixed = TRUE) +
  gwesp(0.69, fixed = TRUE) +
  nodecov("Age") +
  absdiff("Age"))})
brnIntStats = lapply(gangSimBrnInt, FUN = function(x){summary(x~edges +
  gwdegree(0.69, fixed = TRUE) +
  gwesp(0.69, fixed = TRUE) +
  nodecov("Age") +
  absdiff("Age"))})
brnInt2Stats = lapply(gangSimBrnInt2, FUN = function(x){summary(x~edges +
  gwdegree(0.69, fixed = TRUE) +
  gwesp(0.69, fixed = TRUE) +
  nodecov("Age") +
  absdiff("Age"))})

# grab the simulated statistics
grabPar = function(statList, parInd){
  unlist(lapply(statList, FUN = function(x){x[parInd]}))
}

# and do this for all the lists
defEdges = grabPar(defStats, 1)
brnEdges = grabPar(brnStats, 1)
brnIntEdges = grabPar(brnIntStats, 1)
brnInt2Edges = grabPar(brnInt2Stats, 1)

defGwdeg = grabPar(defStats, 2)
brnGwdeg = grabPar(brnStats, 2)
brnIntGwdeg = grabPar(brnIntStats, 2)
brnInt2Gwdeg = grabPar(brnInt2Stats, 2)

defGwesp = grabPar(defStats, 3)
brnGwesp = grabPar(brnStats, 3)
brnIntGwesp = grabPar(brnIntStats, 3)
brnInt2Gwesp = grabPar(brnInt2Stats, 3)

defAgecov = grabPar(defStats, 4)
brnAgecov = grabPar(brnStats, 4)
brnIntAgecov = grabPar(brnIntStats, 4)
brnInt2Agecov = grabPar(brnInt2Stats, 4)


defAgediff = grabPar(defStats, 5)
brnAgediff = grabPar(brnStats, 5)
brnIntAgediff = grabPar(brnIntStats, 5)
brnInt2Agediff = grabPar(brnInt2Stats, 5)

```


```{r plot}
# plot and check
plot(density(defEdges), main = paste("default edges, sd =", sd(defEdges)))
abline(v = trueStats[1], col = "red")

plot(density(brnEdges), main = paste("brn edges, sd =", sd(brnEdges)))
abline(v = trueStats[1], col = "red")

plot(density(brnIntEdges), main = paste("brnInt edges, sd =", sd(brnIntEdges)))
abline(v = trueStats[1], col = "red")

plot(density(brnInt2Edges), main = paste("brnInt2 edges, sd =", sd(brnInt2Edges)))
abline(v = trueStats[1], col = "red")

# gwdeg stats
plot(density(defGwdeg), main = paste("default gwdeg, sd =", sd(defGwdeg)))
abline(v = trueStats[2], col = "red")

plot(density(brnGwdeg), main = paste("brn gwdeg, sd =", sd(brnGwdeg)))
abline(v = trueStats[2], col = "red")

plot(density(brnIntGwdeg), main = paste("brnInt gwdeg, sd =", sd(brnIntGwdeg)))
abline(v = trueStats[2], col = "red")

plot(density(brnInt2Gwdeg), main = paste("brnInt2 gwdeg, sd =", sd(brnInt2Gwdeg)))
abline(v = trueStats[2], col = "red")

# gwesp stats
plot(density(defGwesp), main = paste("default gwesp, sd =", sd(defGwesp)))
abline(v = trueStats[3], col = "red")

plot(density(brnGwesp), main = paste("brn gwesp, sd =", sd(brnGwesp)))
abline(v = trueStats[3], col = "red")

plot(density(brnIntGwesp), main = paste("brnInt gwesp, sd =", sd(brnIntGwesp)))
abline(v = trueStats[3], col = "red")

plot(density(brnInt2Gwesp), main = paste("brnInt2 gwesp, sd =", sd(brnInt2Gwesp)))
abline(v = trueStats[3], col = "red")

# agecov stats
plot(density(defAgecov), main = paste("default agecov, sd =", sd(defAgecov)))
abline(v = trueStats[4], col = "red")

plot(density(brnAgecov), main = paste("brn agecov, sd =", sd(brnAgecov)))
abline(v = trueStats[4], col = "red")

plot(density(brnIntAgecov), main = paste("brnInt agecov, sd =", sd(brnIntAgecov)))
abline(v = trueStats[4], col = "red")

plot(density(brnInt2Agecov), main = paste("brnInt2 agecov, sd =", sd(brnInt2Agecov)))
abline(v = trueStats[4], col = "red")

# agediff stats
plot(density(defAgediff), main = paste("default agediff, sd =", sd(defAgediff)))
abline(v = trueStats[5], col = "red")

plot(density(brnAgediff), main = paste("brn agediff, sd =", sd(brnAgediff)))
abline(v = trueStats[5], col = "red")

plot(density(brnIntAgediff), main = paste("brnInt agediff, sd =", sd(brnIntAgediff)))
abline(v = trueStats[5], col = "red")

plot(density(brnInt2Agediff), main = paste("brnInt2 agediff, sd =", sd(brnInt2Agediff)))
abline(v = trueStats[5], col = "red")

```